# Week 4 Short Answer Questions

## Phuc Nguyen

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

##8.1
1. construct the graphic frame: ggplot()
2. add a layer of glyphs: geom_point(), geom_segment(), geom_histogram()
3. set an axis label: ylab(), xlim()
4. divide the frame into facets: facet_wrap()
5. change the scale for the frame: scale_y_log10()

##8.2
1.
```{r}
mosaicData::CPS85 %>%
  ggplot(aes(age,wage)) + geom_point(aes(shape = married)) + facet_wrap(~sector)

```
2.
```{r}
mosaicData::CPS85 %>%
  ggplot(aes(age, wage)) + geom_point() + facet_grid(sex~married)
```

##8.3
(A)
```{r}
mosaicData::CPS85 %>%
  ggplot(aes(age, wage)) + geom_point()
```

(B)
```{r}
mosaicData::CPS85 %>%
  ggplot(aes(age, wage)) + geom_point(aes(shape = sex))
```

(C)
```{r}
mosaicData::CPS85 %>%
  ggplot(aes(age, wage)) + geom_point(aes(shape = sex)) + facet_grid(married~.)
```

(D)
```{r}
mosaicData::CPS85 %>%
  ggplot(aes(age, wage)) + geom_point(aes(shape = married))
```

##9.1
a. str(): quick presentation
b. group_by(): data verb
c. rank(): comparison expression
d. mean(): summary function
e. filter(): data verb
f. summary(): quick presentation
g. summarise(): data verb
h. anti_join(): data verb
i. glimpse(): quick presentation

##9.3
1. Which color larges on avg
```{r}
diamonds %>%
  group_by(color) %>%
  summarise(avg_carat = mean(carat)) %>%
  arrange(desc(avg_carat)) %>%
  head(1)
```

2. Which clarity has largest avg table per carat
```{r}
diamonds %>%
  group_by(clarity) %>%
  mutate(table_per_carat = table/carat) %>%
  summarise(mean_table = mean(table_per_carat)) %>%
  arrange(desc(mean_table)) %>%
  head(1)
```