# Week 7 Short Answer Questions

## Josh Marcus

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```

```{r}
library(lubridate)
```

<!-- put your content after this line -->

##Chapter 15
###15.1

For the record, I was born on December 2, 1994.

* April 30, 1777, a difference of 79,493 days! 
```{r}
lubridate::mdy("December 2, 1994") -
  lubridate::mdy("April 30, 1777")
```

* 06-23-1912, a difference of 30,112 days!
```{r}
lubridate::mdy("12-02-1994") -
  lubridate::mdy("06-23-1912")
```

* 3 March 1847, a difference of 53,965 days!
```{r}
lubridate::dmy("2 December 1994") -
  lubridate::dmy("3 March 1847")
```

* "11 am on Nov. 11th, 1918 at 11:00 am," a time difference of 27,780. Full disclosure, I have no idea in what hour I was born.
```{r}
lubridate::mdy_hm("Dec. 2, 1994 at 11:00 am") -
  lubridate::mdy_hm("11 am on Nov. 11th, 1918 at 11:00 am")
```

* "July 20, 1969," a difference of 9266 days.
```{r}
lubridate::mdy("December 2, 1994") -
  lubridate::mdy("July 20, 1969")
```

###15.2
* a, "42,659.30," as.numeric() works.
* b, "17%" tidyr::extract_numeric() works.
* c, "Nineteen" Neither works here. We want to use as.character().
* d, "£100" tidyr::extract_numeric() works.
* e, "9.8 m/seconds-square" tidyr::extract_numeric() works.
* f, "9.8 m/s^2" tidyr::extract_numeric() works. 
* g, "6.62606957 x 10^-34 m2 kg / s" tidyr::extract_numeric() works.
* h, "6.62606957e-34" tidyr::extract_numeric() works.
* i, "42.659,30," as.numeric works.

##Chapter 16
###16.
1. 
```{r}
BabyNames %>%
  filter(sex == "M") %>%
  group_by(name) %>%
  summarise(total = sum(count)) %>%
  filter(grepl("[aeiou]$", name)) %>%
  arrange(desc(total)) %>%
  head(10)
```
2. 
```{r}
BabyNames %>%
  group_by(name) %>%
  summarise(total = sum(count)) %>%
  filter(grepl(".*(jo$|joe$)", name)) %>% 
  arrange(desc(total)) %>%
  head(10)
```

###16.2
This entire general expression matches U.S. phone numbers. The ([2-9] [0-9] {2}) is the area code, the [- .] is the punctuation that seperates it from the main number, and the ([0-9]{3})[- .]([0-9]{4}) is the rest of the number.

###16.3
1. They will be two letters.
2. The number of strings that will match is equal to the number of different letters inside the brackets. So, fo C[AOT], there are three patterns that match, for D[EC] there are two, and so on.
3. These are abbreviations for U.S. states and territories.
