# Week 5 Short Answer Questions

## Your name should appear here!

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

Here is my content!


10.1

we are joining two tables, so we need another table in our argument.


10.2

The individual cases in two tables are not one-to-one. They are different things. Can't put information of different things together and call it one thing.


10.3

Table B. mutate(diff=Y2001-Y2000)

Table C. left join, followed by a group_by sum


11.1

One: numer of babiies of a name in a year with a sex

Two: number of babies of a name in a year of each sex respectively

Three: numer of babiies of a name of a sex in each one of the two year options

One is narrow. Two is wide.

Key: sex. Value: nbabies.

Some names do not have one of the two sex in some years. In narrow form, these cases are excluded.

By being wider.

year

F, M

sex

nbabies


11.3

A is wide and C is narrow

B is wide and C is narrow


11.5

```{r}
load(url("http://tiny.cc/dcf/MeasTreatTables.rda"))

Combined <-
  Measurements %>%
  left_join(Treatments,"subject"="subject") 

Reconstruction <-
  Combined %>%
  mutate(when=ifelse(date<=treatment_date,"before","after")) %>%
  spread(key=what,value=value) %>%
  select(subject,when,sbp,dbp,date)

head(Reconstruction)

```
