# Week 4 Short Answer Questions

## Katie Jolly

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(ggplot2)
library(mosaicData)
```
<!-- put your content after this line -->

## 8.1

1. ggplot()

2. geom_point(), geom_segment(), geom_histogram()

3. ylab()

4. facet_wrap()

5. xlim(), scale_y_log()

## 8.2


### 1

```{r}
ggplot(CPS85, aes(x= age, y= wage, shape= married)) + geom_point() + facet_wrap(~sector) + ylim(0, 30)
```

### 2

```{r}
ggplot(CPS85, aes(x= age, y= wage)) + geom_point() + facet_grid(sex ~ married)
```


## 8.3

### A

```{r}
ggplot(CPS85, aes(x= age, y= wage)) + geom_point()
```

### B

```{r}
ggplot(CPS85, aes(x= age, y= wage, shape= sex)) + geom_point()
```

### C

```{r}
ggplot(CPS85, aes(x= age, y= wage, shape= sex)) + geom_point() + facet_grid( married ~ .)
```

### D

```{r}
ggplot(CPS85, aes(x= age, y= wage, shape= married)) + geom_point() + ylim(0,30)
```

## 9.1

a. str() is a summary verb

b. group_by is a data verb

c. rank() is quick presentation 

d. mean() is a summary function

e. filter() is a data verb

f. summary() is a summary function

g. summarise() is a data verb

h. anti_join() is a data verb

i. glimpse() is a data verb

## 9.3 

```{r}
diamonds %>% group_by(color) %>% arrange(desc(carat)) %>% head(1)
```

```{r}
diamonds$TableperCarat <- diamonds$table/diamonds$carat
diamonds %>% group_by(clarity) %>% arrange(desc(TableperCarat)) %>% head(1)
                                              
```

