# Week 7 Short Answer Questions

## Phuc Nguyen

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

##15.1
```{r}
my_bd <- lubridate::dmy("6 March 1996")
a <- lubridate::mdy("April 30, 1777")
my_bd - a
b <- lubridate::mdy("06-23-1912")
my_bd - b
c <- lubridate::dmy("3 March 1847")
my_bd - c
d <- lubridate::mdy_hm("11:00 am on Nov. 11th, 1918 at 11:00 am")
my_bd - d
e <- lubridate::mdy("July 20, 1960")
my_bd - e
```

##15.2
a. tidyr::extract_numeric()
b. tidyr::extract_numeric()
c. none
d. tidyr::extract_numeric()
e. tidyr::extract_numeric()
f. tidyr::extract_numeric()
g. tidyr::extract_numeric()
h. as.numeric
i. tidyr::extract_numeric()

##16.1
```{r}
pattern <- "[aeiou]$"
BabyNames %>%
  group_by(name) %>%
  filter(sex == "M" & grepl(pattern, name)) %>%
  summarise(total = sum(count))%>%
  arrange(desc(total)) %>%
  head(10)
```

```{r}
pattern <- "joe$|jo$"
joe <- BabyNames %>%
  filter(grepl(pattern, tolower(name)))
head(joe)
```

##16.2
The regular expression extracts phone numbers. The numbers are the only components to be extracted.

##16.3
The strings can be any length greater or equal to two (letters).
