# Week 6 Short Answer Questions

## Daniel Ochoa

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

## 12.1
```{r}
Top5Names <- BabyNames %>%
  group_by(sex, name) %>%
  summarise(total=sum(count)) %>%
  filter(rank(desc(total)) <= 5)


print(Top5Names)
```


## 12.2
```{r}
PopularCounts <- BabyNames %>%
  group_by(year, name) %>%
  summarise(total = sum(count))

PopularCounts <- PopularCounts %>% 
  mutate(frac_in_top_100 = rank(desc(total)))

PopularCounts$frac_in_top_100 <- ifelse(PopularCounts$frac_in_top_100 <=100,"True","False")
GlyphReady <-
  PopularCounts %>%
  group_by(year, frac_in_top_100) %>%
  summarise(Total = sum(total)) %>%
  spread(frac_in_top_100, Total) %>%
  mutate(frac_in_top_100= `True` / (`True` + `False`))
GlyphReady %>%
  ggplot(aes(x=year, y=frac_in_top_100)) +
  geom_line () +
  ylim(0,NA)

print(GlyphReady)

```


## 12.3
a) summary
b) neither because this involves a pair of values.
c) summary
d) transformation
e) transformation
f) summary
g) transformation
h) summary


## 13.1
1) 7
2) 9


## 13.2
1) ABCD
2) 2
3) Table 1 doesn't show the edge between c and d, and shows there's an edge between b and c which is false. Table 3 has 3 objects in one row.


## 13.3
Table 2

## 13.4
1. Exports
2. Population

## 14.1
```{r}
mosaicData::CPS85 %>%
  ggplot(aes(y = wage, x = sex)) +
  geom_boxplot(aes(fill=sex))
```


## 14.3
women = 1.6 meters, men = 1.75 meters

## 14.7
```{r}
mosaicData::CPS85 %>%
  ggplot( x = educ, y = wage, color = sex) + geom_point() +
  stat_smooth(method="1m") +
  ylim(0,15)

```


## 14.10
```{r}

mosaicData::Galton %>%
  ggplot(aes(x = height, group = sex)) +
  geom_density(aes(color = sex, fill = sex), alpha = 0.5) +
  xlab("height") + ylab("density")

```
