# Week 7 Short Answer Questions

## Lang Li

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```

# Problem 15.1
My birthday is March 28, 1996
```{r}
LL_Bday <- lubridate::ymd("1996-3-28")
Gauss <- lubridate::mdy("April 30, 1777")
Turing <- lubridate::mdy("06-23-1912")
Bell <- lubridate::dmy("3 March 1847")
WWI<- lubridate::mdy_hm("Nov. 11th, 1918 at 11:00 am")
Moonlanding <- lubridate::mdy("July 20, 1969")
```

Gauss:
```{r}
Gauss
LL_Bday-Gauss
```

Turing:
```{r}
Turing
LL_Bday - Turing
```

Bell
```{r}
Bell
LL_Bday - Bell
```

World War i
```{r}
WWI
LL_Bday - WWI
```

Moon landing
```{r}
Moonlanding
LL_Bday - lubridate::date(Moonlanding)
```

# Problem 15.2

a. as.numeric returns NA but extract_number, which is now readr::parse_number works pretty well

b. as.numeric returns NA but extract_number works well.

c. Both cannot work well.

d. as.numeric returns NA but extract_number works well.

e. as.numeric returns NA but extract_number works well.

f. as.numeric returns NA but extract_number works well. 

g. They both cannot work really well.

h. as.numeric returns the correct one but the other one does not work well

i.  as.numeric returns NA but extract_number works well. 

# Problem 16.1

1. 
```{r}
BabyNames %>% filter(sex == "M") %>% group_by(name) %>%
summarise(total = sum(count)) %>% filter(grepl("[aeiou]$",name)) %>%
  arrange(desc(total))%>%head(10)
```

2. 
```{r}
BabyNames %>% group_by(name) %>% summarise(total = sum(count)) %>% filter(grepl(".*(jo$|joe$)", name)) %>% arrange(desc(total))
```

# Problem 16.2

This is a telephone number for sure. The component that is being extracted is the number portion of the regex. By extracting those things, you can call someone else.

# Problem 16.3

1. The string should have a length of 2 to match.

2. 61 Strings will be matched.

3. It is the U.S States and Territories (even includes army....) Abbreviation. 
