# Week 3 Short Answer Questions

## Your name should appear here!

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->
```{r echo=FALSE}
options(warn=-1)
```

# Problem 5.1
```{r}
library(mosaicData)
library(DataComputing)
ggplot(data=CPS85,aes(x=sex,y=wage ,fill=married))+geom_bar(stat='identity',position='dodge', width=.9)+ facet_wrap(~race,ncol=3) 
```

# Problem 5.2
```{r}
HappinessIndex %>% WorldMap(key = "country", fill = "corruption")
```

# Problem 6.5

b. State and Polling Organization 

# Problem 6.6

d. Glyph: Rectangle; Graphical Attributes: Color and Texts

# Problem 6.7 

d. NYT Poll probability for the Democratic candidate

# Problem 6.8

```{r}
Small <- NCHS %>% sample_n(size = 5000)
ggplot(data=Small,aes(x=bmi,y=weight))+geom_point()+aes(colour=smoker) 
```

The variable is mapped based on the weight~BMI relationship and the graphical attributes of different color illustrates the population of smokers and non-smokers

# Problem 7.1

a. summarise()

b. mutate()

c. arrange()

d. filter()

e. select()

f. group_by() and summarise()

# Problem 7.4

a. Inside the function group_by() should be a variable name. There is no variable name called "First" in the data set.

b. You cannot summarise "Tmp" at the time you create it as an object.

c. These are two separate line of code. The summary provided does not reveal the property of Tmp but the whole data set.

# Problem 7.5 

a. So this one arranges the data by looking at the sex and the count, so the code could be:  BabyNames %>% arrange(sex, count)



b. This one select all the females, so it is a filtering process, the code could be: 
BabyNames %>% filter (sex == "F")



c. So this one chooses the male and get all the names that appears more than certain times. The correct code is: BabyNames %>% filter (sex == "M", count > 9)


d. This one simply counts the number of cases in the data frame: BabyNames %>% summarise (total = sum(count))


e. This one count the number of times that each name appears: BabyNames %>% select(name, count)


# Problem 7.7

a. You should delete the Babynames in the summarise method, the correct code should be:
BabyNames %>% group_by(year, sex) %>% summarise(total = sum(count))

b. ZipGeography is not a object but a data set, so you want to associate with it and use the data inside of it rather than give it a value to store in, the correct code is:
ZipGeography %>% group_by(State) %>% summarise(pop = sum(Population))

c.'->' is illegal, use "%>%" instead, the correct code should be:
Minneapolis2013 %>% group_by(First)%>% summarise(voteReceived = n())

d. The order of the command seems not correct, and see c for the correct version.

# Problem 7.11

a. sex, count, meanAge.

b. diagnosis, count, meanAge.

c. sex, diagnosis, count, meanAge.

d. age,  diagnosis, count, meanAge.

e. age, count, meanAge.

# Problem 7.12

a. nrow()

b. names()

c. help()

d. library()

e. group_by()

f. summarise()