# Week 3 Project

## HENRY ZUO!! 

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(mosaicData)
library(ggplot2)
```
<!-- put your content after this line -->

Here is my content!

What mode of grpahics is it?
Figure 1 is a scatter plot with 8 different facets
Figure 2 is a density plot with 2 facets

What variables from the respective data tables are involved?
Figure 1 involves 4 variables: marriage status, profession, years of experience, and wage.
Figure 2 involes 3 variables: sex, bmi, pregnancy

What role does each of those variables play in the graphics?
Figure 1 variables demonstrate whether marrital status influence the relationship between wage and experience across different professions
Figure 2 variables demonstrate if gender and pregnancy play a role in determining people's BMI

In Figure 2, why is there no data variable being used for the y-axis?
Y-axis is used to show count of cases, so no variables can be used.


```{r}
ggplot(data=CPS85,aes(x=educ,y=wage))+geom_point()+aes(colour=sex)+facet_wrap(~union,ncol=4)
ggplot(data=CPS85,aes(x=educ))+geom_density(aes(color=sex))+facet_wrap(~union,ncol=4)
```




Diamonds




Which color diamonds seem to be largest on average (in terms of carats)?
```{r}
diamonds %>% group_by(color) %>% summarize(mn=mean(carat)) %>% arrange(desc(mn)) %>% head(1)
```
As shown, color J has the largest carat on average.

Which clarity of diamonds has the largest average "table" per carat?
```{r}
diamonds %>% mutate(var=table/carat) %>% group_by(clarity) %>% summarize(mn=mean(var)) %>% arrange(desc(mn)) %>% head(1)
```
As shown, clarity VVS1 has the largest average table per carat.




Voting




How many cases are there?
```{r}
nrow(Minneapolis2013)
```
80101 cases are in the dataset

Who were the top 5 candidates in the Second vote selections?
```{r}
Minneapolis2013 %>% group_by(Second) %>% tally() %>% arrange(desc(n))
```
As shown, top 5 candidates in the Second vote selections are BETSY HODGES, DON SAMUELS, MARK ANDREW, JACKIE CHERRYHOMES, BOB FINE

How many ballots are marked "undervote" in First, Second, and Third?
```{r}
Minneapolis2013 %>% group_by(First) %>% tally() %>% filter(First=="undervote")
Minneapolis2013 %>% group_by(Second) %>% tally() %>% filter(Second=="undervote")
Minneapolis2013 %>% group_by(Third) %>% tally() %>% filter(Third=="undervote")
```
The counts are 834, 10598, and 19210 respectively

What are the top 3 Second vote selections among people who voted for Betsy Hodges as their first choice?
```{r}
Minneapolis2013 %>% filter(First=="BETSY HODGES") %>% group_by(Second) %>% tally() %>% arrange(desc(n)) %>% head(3)
```
They are MARK ANDREW, DON SAMUELS, and JACKIE CHERRYHOMES

Which Precinct had the highest fraction of First vote selections marked as "undervote"?
```{r}
Minneapolis2013 %>% group_by(Precinct) %>% summarise(pc=mean(First=="undervote")) %>% arrange(desc(pc)) %>% head(1)
```
Precinct P-6C had the highest fraction.

