# Week 2 Short Answer Questions

## Joseph Goodson-Gregg!

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

Here is my content!

Chapter 1: (1.1, 1.2, 1.4, 1.5)
Problem 1.1
a. 1
b. 2
c. 1
d. 1
e. 3

Problem 1.2
In the 'president' column, the names do not follow the same pattern. Lincoln, Abraham has the format: last, first, in contrast to George Washington which follows the format: first, last.

Similarly, the values for the 'in office' column, the formatting for year ranges is inconsistent. 1791-1799 and 1837-1841 are different formats.

Further in the 'number of states' column categorical and quantitative values are mixed. 'it depends' and '16' should not be part of the same column.

Problem 1.4
1. 
Data Table A: Year, Algeria, Brazil, Columbia.
Data Table B: Country, Y2000, Y2001.
Data Table C: Country, Year, Value.

2.
Data Table A: A year.
Data Table B: A country.
Data Table C: A country in a year.

Problem 1.5
1. 6.
2. The cases represent specific airports.
3. 
faa: possesses categorical.
name: categorical.
lat,lon: quantitative.
alt: quantitative.
tz: quantitative.
dst: categorical.

_____________

Chapter 2: (2.2, 2.3, 2.4, 2.6, 2.7, 2.8, 2.8, 2.9, 2.10)
Problem 2.2:
2.

Problem 2.3:
The Current Population Survey is a supplement to census information between years. It is random sampling info on characteristics of workers.

Problem 2.4:*
help(NHANES, package <- "NHANES")
I am unsure on this one. 
Perhaps it is poor form to assign the package inside the function, although after testing this doesn't seem to be the likely reason.
When I tested this function it worked fine.View

Problem 2.6:
1. Legitimate.
2. Not legitimate. Punctuation is included (hyphen).
3. Not legitimate. Punctuation is included (quotation marks).
4. Legitimate.
5. Not legitimate. Punctuation is included (space).
6. Legitimate.
7. Legitimate.
8. Legitimate.
9. Not legitimate, this is a function.

Problem 2.7:
1. 19.
2. 336,776.
3. Flights departing from NYC on-time for 2013.
4.
year: quantitative.
month: quantitative.
day: quantitative.
dep_time: quantitative.
sched_dep_time: quantitative.
dep_delay: quantitative.
arr_time: quantitative.
sched_arr_time: quantitative.
arr_delay: quantitative.
carrier: categorical.
flight: quantitative.
tailnum: categorical.
origin: categorical.
dest: categorical.
air_time: quantitative.
distance: quantitative.
hour: quantitative.
minute: quantitative.
time_hour: categorical.

Problem 2.8:
a. 3.
b. 1.
c. 4.
d. 2.
e. 3.

Problem 2.9:
1. _ and .
2. All can be used.

Problem 2.10:
1. 75.
2. 256.
3. Mass of trunk fat.
4. 23,018.
5. Count.
6. UNA, DEM, REP, LIB. Respectively: Unaffiliated, Democratic, Republican, Libertarian.

Chapter 3: (3.1, 3.2, 3.3, 3.4, 3.5, 3.6)
Problem 3.1:
1. Babynames %>%...
2. sum(example)
3. namedargument = sum(example)
4. sum(variable)

Problem 3.2:
Chaining together a statement that is already non-chaining syntax is improper.
Babynames %>%...
or 
Result <- filter... 
would be fine. But not together.

Problem 3.3:
I am still unsure. This problem is a repeat of a chapter 2 problem.

Problem 3.4:
1. b.
2. a.
3. d.
4. a.
5. a.
6. c.
7. c.
8. a.
9. d.
10. a.
11. c.
12. c.
13. a.
14. c.
15. c.
16. a.
17. c.
18. a.
19. c.

Problem 3.5:
1. The weight of brain in kg.
2. 83.
3. These are for species of animal.
4. insectivore, carnivore, herbivore, carnivore, NA.

Problem 3.6:
c.

Chapter 4: (4.1, 4.2, 4.3, 4.4, 4.5)
4.1
*one* is italicized
**two** is bold
* three is a bulleted part of an unordered list
# four is header type 1
`five` is inline r code
## six is header type 2
[seven](http://tiny.cc/dcf/index.html) is a link with a corresponding url


4.2
a. uses ' instead of ` for its r chunk
b. uses " instead of ` for its r chunk
c. is missing a ` at the end of its r chunk
d. Does not have proper \n (newline character) formatting
e. has an extra ` at the end of its r chunk


4.3
It will look like
HEADER An Introduction


Arithmetic is easy(italics)! For instance
3+2
5

### An Introduction

Arithmetic is *easy*! For instance
```{r}
3+2
```




4.4
1. Possible URL
2. Possible file
3. Neither
4. Possible URL
5. Neither
6. Possible URL

4.5
# Copied from original file, which looks exactly as it should. (If pasted into a new file it will work great.)
---
title: "Birds of the World"
author: "JJ Audobon"
output: 
  html_document:
    fig_height: 3
    fig_width: 5
---
<!-- Don't edit in between this line and the one below -->
```{r include=FALSE}
# Don't delete this chunk if you are using the DataComputing package
library(DataComputing)
```
*Source file* 
```{r, results='asis', echo=FALSE}
includeSourceDocuments()
```
<!-- Don't edit the material above this line -->


There are many species of birds in the world. From my studio, I can see

* Blue Jays
* Cardinals
* Robins
* Crows
* Sparrows


