# Week 3 Short Answer Questions

## Shelby Witherby

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(ggplot2)
```
<!-- put your content after this line -->

## 5.1:
```{r}

library(DataComputing)
library(mosaicData)



```

```{r}

ggplot(data = CPS85, aes(x = sex, y = wage)) + facet_wrap(~ married) + geom_point()

```

## 5.2
```{r}

HappinessIndex %>%
  WorldMap(key = "country", fill = "corruption")

```

## 6.5
 b
 
## 6.6
 d
 
## 6.7
d

## 7.1
a. summarise( ave = mean())
b. mutate
c. arrange(desc())
d. filter()
e. select
f. mutate

## 7.5
a. arrange(sex, count)
b. filter(sex = M)
c. filter(sex = F)
d. n(row)
e. select(name, count)

## 7.11
a. mean age of each sex, total count of each sex
b. mean age of each diagnosis, total count of each diagnosis
c. mean age of each group of sex&diagnosis, with a count of each category
d. count of every age group, mean age

##7.12
1. n(row)
2. summarise
3. help
4. library()
5. group_By
6. summarise(totalPop = sum())
