# Week 2 Short Answer Questions

## Katrin O'Grady

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

###Problem 1.1
a) Taffy- value of the variable for a particular case
b) year- quantitative variable
c) sex- categorical variable
d) name- categorical variable
e) count- quantitative variable

###Problem 1.2
The number of states variable is neither quanitative nor categorical. Most of the values are numbers but one of them is "it depends" do the values are not uniform.

###Problem 1.4
The variables in A are year, Algeria, Brazil, and Coumbia. In B they are country, 2000, and 2001. In C they are country, year, and value. For A, a case is a year. For B a case is a country in a year, and for C, a case is a country.
###Problem 2.2
The name of an argument in a named argument.
###Problem 2.3
CPS stands for current population survey.
###Problem 2.4
You don't need to use the naming function of package <- "NHANES" within the help function. If you've already introduced and downdloaded the package to r, you can just input help("NHANES")
###Problem 2.6
essay14 - legitimate
first-essay - can't use a - symbol
"MyData" - don't need ""
third_essay - legitimate
small smaple - can't use a space
functionList - legitimate
FuNcTi0nLiSt - legitimate
.MyData. - legitimate
sqrt() - can't use ()
###Problem 2.7
```{r}
install.packages("nycflights13")
data(flights, package = "nycflights13")
```
1. 19 variables
2. 336773 cases
3. a case is a specific flight
4. all of the variables are quantitative except for origin, tailnumber, destination, carrier
###Problem 2.8
a. improper syntax for function argument
b. no assignment operator
c. invalid object name
d. unmatched quotes in character string
e. no mistake
###Problem 2.9
in an object name a . and an _ can be used. In a quoted character string all can be used.
###Problem 2.10
- 75 variables
- mass of trunk fat
- 23018 cases
- count
- DEM=Democratic, LIB=Libertarian,REP=Republican,UNA=Unaffiliated
###Problem 3.1
1. Fireplace %>%
2. fireplace()
3. "fireplace"
4. (fireplace)
###Problem 3.2
Before the %>%, there needs to be the name of the data set, and that is missing in this sentence. 
###Problem 3.3
The package <- "NHANES" is not necessary in this statment. You should introduce the data first and then just input help(NHANES)
###Problem 3.5
- brain weight in kilograms
- 83 cases
- a species of mammal 
- carnivore, omnivore, or herbivore
###Problem 3.6
Statement a. 
###Problem 4.1
- *one* is in italics
- **two** is bolded
- *three moves to the line above it
- #Four - four will become the largest section heading
- `five`has no change
- ##six - six will become the second largest section heading

###Problem 4.2
a) the wrong dashes are used
b) the wrong parenthesis are used
c) only 2 dashes are used on teh bottom
d) the second three dashes should be underneath the top level with the input in between
e) there are four dashes in the bottom layer
###Problem 4.3
The introduction would be the heading. 
Underneath, the word easy would be in italics. Then, the 3+2 would appear in a box and the answer 5 would appear below in another box



