# Week 3 Short Answer Questions

## Daniel Ochoa

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(mosaicData)
library(ggplot2)
```
<!-- put your content after this line -->

###Question 5.1
```{r}
ggplot(data=CPS85,aes(x=sex,y=wage ,fill=married))+geom_bar(stat='identity',position='dodge', width=.9)+ facet_wrap(~race,ncol=3)

```

###Question 5.2

```{r}
HappinessIndex %>%
  WorldMap(key = "country", fill = "corruption")
```

###Question 6.5

b

###Question 6.6

d

###Question 6.7

d

###Question 6.8

```{r}
Small <-
  NCHS %>%
  sample_n(size=5000)
```

```{r}
ggplot(data=Small,aes(x=bmi,y=weight))+geom_point()+aes(colour=smoker)
```

### Question 7.1


a) summarise(mean())

b) mutate()

c) arrange(desc())

d) filter()

e) select()

f) mutate()

### Question 7.4

a) "First" is not a variable in BabyNames

b) The pipe is used wrongly.

c) Have to summarise Tmp, not BabyNames


### Question 7.5

a) arrange(sex, count)

b) filter(sex = M)

c) filter(sex = F)

d) n(row)

e) select(name, count)



### Question 7.7

a) Shouldn't have BabyNames in the summarise function.

b) Missing a pipe in the first line.

c) Missing a pipe in the second line. SHould not have an assignment operator.

d) Minneapolis2013 should be at the beginning, not at the end.

### Question 7.11

a) total count of each sex, mean age of each sex.

b) total count of each diagnosis, the average age at which someone gets each diagnosis.

c) number of people of each sex that get each diagnosis, mean age of each diagnosis for both sexes.

d) number of people of each age that get each diagnosis, mean age of each diagnosis.

e) number of people of each age, and that age.


### Question 7.12

1) nrow()

2) summarise()

3) help

4) library()

5) group_By

6) tally()
