# Week 6 Short Answer Questions

## Joseph Goodson-Gregg

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

Here is my content!

Chapter 12 Questions: (12.1, 12.2, 12.3)

12.1
```{r}
BabyNames %>%
  group_by(name) %>%
  filter(sex == "M") %>%
  summarise(total = sum(count)) %>%
  arrange(desc(total)) %>%
  head(5)
```
```{r}
BabyNames %>%
  group_by(name) %>%
  filter(sex == "F") %>%
  summarise(total = sum(count)) %>%
  arrange(desc(total)) %>%
  head(5)
```

12.2

```{r}
tabletwelvetwo <-
  BabyNames %>%
  group_by(year) %>%
  mutate(frac_in_top_100 = rank(desc(count)) <= 100)

tabletwelvetwo %>%
  head(5)
```

```{r}
tabletwelvetwo <-
  tabletwelvetwo %>%
  group_by(year, frac_in_top_100) %>%
  summarise(total = sum(count))

tabletwelvetwo %>%
  head(5)
```

```{r}
GlyphReady <-
tabletwelvetwo %>%
  spread(frac_in_top_100, total) %>%
  mutate(frac_in_top_100 = (`TRUE`/(`TRUE`+`FALSE`)))
         
GlyphReady %>%
  head(5)
```

12.3

a. summary

b. summary

c. summary

d. transform

e. transform

f. summarise

g. transform

h. summarise

Chapter 13 Questions: (13.1, 13.2, 13.3, 13.4)
13.1

part 1: 8

part 2: 9

13.2

part 1: A, B, C, D

part 2: Table 2

part 3: Table 1 incorrectly shows an edge between B and C instead of C and D. Table 3 improperly shows an edge as connections between three vertices instead of two.

13.3

Table 2

13.4

part 1: exports

part 2: pop

Chapter 14 Questions: (14.1, 14.3, 14.7, 14.10)

14.1

```{r}
CPS85 %>%
  ggplot(aes(y = wage, x = sex )) +
  geom_boxplot(aes(fill = sex),
               position = position_dodge(width=0.8))
```

14.3

Approximately 1.6 m for women and 1.8 m for men.

14.7

```{r}
CPS85 %>%
  ggplot(aes(x=educ,y=wage))+geom_point()+aes(colour=sex)+stat_smooth(method = lm) +geom_point(alpha = 0.02)+xlim(0,20)+ylim(0,15)
```

14.10

```{r}
mosaicData::Galton %>%
  ggplot(aes(x=height))+geom_density(aes(fill=sex), color=NA)
```

