# Week 6 Short Answer Questions

## Tristan Truttmann

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```

### 12.1 

```{r}
BabyNames %>% 
  group_by(sex,name) %>%
  summarise(count = sum(count)) %>%
  group_by(sex) %>% 
  mutate(TheRank= rank(desc(count))) %>%
  arrange(TheRank) %>%
  head(10)
```

I think the output table says it all.  

### 12.2

```{r}
GlyphReady <- BabyNames %>%
  spread(key = sex, value = count) %>% 
  mutate(total = ifelse(is.na(F),0,F) + ifelse(is.na(M),0,M) ) %>% 
  group_by(year)  %>%
  mutate(TheRank = row_number(desc(total)) ) %>%
  mutate(intop100 = (TheRank < 101)) %>% 
  arrange(TheRank) %>% 
  summarise(frac_in_top100 = sum(intop100)/n()) %>% 
  arrange(year)
```

Now I can graph this stuff: 

```{r}
GlyphReady %>%
  ggplot() +
  geom_point(aes(x=year,y=frac_in_top100))
```

### 12.3

(a) A transformation function. 
(b) Transformation
(c) summary
(d) transformation if each case is a year.  If year is a variable and the case is a day, then it would probably be a summary function. 
(e) tansformation
(f) summary
(g) transformation
(h) summary
(e)

### 13.1 

(1) There are 7 distinct verticies. 
(2) There are 9 edges. 

### 13.2

(1) The verticies are A, B, C, D. 
(2) Only Table 2 shoes the edges correctly. 
(3) Table 1 shoes a connection between B and C which doesn't exists. Table 3 has 3 columns, which I don't know how to interpret. 

### 13.3 

Only Table 2 provides sufficient information. 

### 13.4 

(1) `exports` is mapped to the shape. 
(2) `pop` is mapped to the shape of the gray symbol. 

### 14.1

```{r}
CPS85 %>%
  ggplot(aes(x=sex,y=wage)) + 
  geom_boxplot()
```

I didn't shade the boxes to stay within the time limit. 

### 14.3

The most likely height for men is about 1.8 meters.  The most likely hieght for women is about 1.6 meters. 

### 14.7

```{r}
CPS85 %>%
  ggplot(aes(x=educ,y=wage)) + 
  geom_point(aes(color=sex)) + 
  stat_smooth(method=lm,aes(color=sex))
```

I'm running close to the time limit so I won't spent time to change to color or the range.  

### 14.10


