# Week 7 Short Answer Questions

## Shelby Witherby

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```

# 15.1
# I was born on April 15, 1996

```{r}

lubridate::mdy("April 15, 1996") - lubridate::mdy("April 30, 1777")

lubridate::mdy("04-15-1996") - lubridate::mdy("06-23-1912")

lubridate::dmy("15 April 1996") - lubridate::dmy("3 March 1847")

lubridate::mdy_hm("Apr. 15, 1996 at 02:00 am") - lubridate::mdy_hm("11 am on Nov. 11th, 1918 at 11:00 am")

lubridate::mdy("April 15, 1994") - lubridate::mdy("July 20, 1969")

```

## 15.2
# a) as.numeric() 
# b) tidyr::extract_numeric()
# c) Neither works. We need to use as.character()
# d) tidyr::extract_numeric()
# e) tidyr::extract_numeric()
# f) tidyr::extract_numeric()
# g) tidyr::extract_numeric()
# h) as.numeric()
# i) as.numeric

## 16

```{r}
BabyNames %>%
  filter(sex == "M") %>%
  group_by(name) %>%
  summarise(total = sum(count)) %>%
  filter(grepl("[aeiou]$", name)) %>%
  arrange(desc(total)) %>%
  head(10)

```

```{r}

BabyNames %>%
  group_by(name) %>%
  summarise(total = sum(count)) %>%
  filter(grepl(".*(jo$|joe$)", name)) %>%
  arrange(desc(total)) %>%
  head(10)

```



## 16.2 
# This matches phone numbers. ([2-9] [0-9] {2}) is the area code, [-.]  separates it from the main number, and ([0-9]{3})-. is the rest of it

## 16.3 
# 1) Two letters
# 2) There appears to be 61 possible combinations
# 3) These are abbreviations for states and territories

