# Week 8 Project

## Daniel Ochoa 

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(ggdendro)
```
<!-- put your content after this line -->

Finding the distances from each car to each other car
```{r}
Dists <- dist(mtcars)
```

Making the dendogram using a clustering algorithm
```{r}
Dendrogram <- hclust(Dists)
ddata <- dendro_data(Dendrogram)
```

Visualizing the data
```{r}
ggdendrogram(Dendrogram, rotate = TRUE) + geom_text(data = ddata$labels, aes(x = x, y = y, label = label), vjust = 0)
```


## Genetics Data

I create a table similar to the Table 2 that is figured in the worksheet
```{r}
Genetics <- 
  NCI60 %>%
  gather(key = cellLine, value = expression, -Probe)
```


I combine it when the same probe appears multiple times on the gene chip.
```{r}
Genetics2 <- 
  Genetics %>%
  group_by(Probe, cellLine) %>%
  summarise(expression = mean(expression)) %>%
  ungroup()
```


Here I alter the genetics table by having a column to include the spread of the data.
```{r}
Genetics3 <- 
  Genetics2 %>%
  group_by(Probe) %>%
  summarise(spread = sd(expression))
```


Here I only consider the probes that has expressions whose standard deviation were above 4.20.
```{r}
Genetics4 <-
  Genetics2 %>%
  group_by(Probe) %>%
  filter(sd(expression) >= 4.20)
```


Here I move the data to a wider format, the data is still filtered so as to only keep expressions whose standard deviation is above 4.20 but now each case is a cellLine.
```{r}
GeneticsWide <-
  Genetics4 %>%
  spread(key = Probe, value = expression) 
row.names(GeneticsWide) <- GeneticsWide$cellLine
```

Here I create all the data step by step that will be necessary for me to create the genetics dendrogram.
```{r}
GeneticDists = dist(GeneticsWide %>% select(-cellLine))
GeneticsDendrogram <- hclust(GeneticDists)
gdata <- dendro_data(GeneticsDendrogram)
```

Finally visalizing the genetics data
```{r}
ggdendrogram(GeneticsDendrogram, rotate = TRUE) + geom_text(data = ddata$labels, aes(x = x, y = y, label = label), vjust = 0)
```

