# Week 5 Short Answer Questions

## Xing Gao

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->
10.1 the reason why join family of data verbs always have a data table inside the parenthesis because it is chaining the new data table to the original one. 

10.2 this cannot be done because the rows won't match up. 

10.3 
a. I think Table B is the easiest. I can just substract the 2000 column from 2001. the command would be TableB %>% mutate(change = (Y2001-Y2000))

b. Table C would be best because we can join the table with continent info to table C, and then calculate the sum of the values for each country, during each year. 
for year 2001:
TableC %>%
left_join(ContinentData)%>%
group_by(country)%>%
filter(Y2001)%>%
summarise(total=sum(value))

for year 2000:
TableC %>%
left_join(ContinentData)%>%
group_by(country)%>%
filter(Y2000)%>%
summarise(total=sum(value))

11.1
a. 
version one: a case shows how many babies, of a certain sex, are born in a particular year and have a particular name
version two: a case shows given a baby and the year, how many babies with that name are amle.female
version three: how many babies with a certain sex and name are born in each year. 
b. Version 1 is narrow, 2 is wide. 
c. sex is the key variable
d. because table two and three are wide tables, and in some cases, the column does not apply to that case. 
e. they contain the same information because in table two, each case is assigned to a particualr year while in table three, each case is assigned to a particular sex
f. year was used to spread one to three


11.3
A. C is narrow, A is wide
B. C is narrow, B is wide
C. C is narrow, A is wide


11.4
the new table will have a column when, with before and after, and the sbp column, plus a subject column. However, the before and after won't be in the right column because the subject column is there. 

11.5
```{r}
download.file("http://tiny.cc/dcf/MeasTreatTables.rda", destfile = "MeasTreatTables.rda")
```


Here is my content!
