# Week 5 Short Answer Questions

## Kai Heen

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->
## 10.1

Join always has a data table as one of its arguments, as it always turns two data tables into one data table.

## 10.2

The two tables cannot be successfully joined becasue the two tables have different numbers of rows. Cases for individual countries are also different. 

##10.3

Data table B.

Data Table B %>% 

    mutate(difference = Y2001 - Y2000)


tableC %>%

  join(ContinentData) %>%
  
  group_by(Continent, Year) %>%
  
  summarise(total = sum(Value))

##11.1 

(A)

1.  Shows number of babies that all have the same sex and name, and were born in the same year.

2. Given a name in a specific year

3. Shows number of babies with a given name of a given sex


(B)

Version 1: narrow 

Version 2: Wide

(C)

Sex is key variable

(D)

Versions 2 and 3 are wide tables. They have to provide information that version 1 can simply not include.


(F) year

(G)

1. M and F are gathered into sex in Version 1. 

2. sex

3. Number of female and male babies/ year.

#11.3

a)

Table A: wide 

Table C: narrow

b)

Table B: wide 

Table C: narrow

c)

Table A: wide 

Table C:narrow

#11.4 

The new table will have two variables, SBP and When.

#11.5
```{r}
data <- load("/home/local/MAC/qsun/Comp-110-Assignments/MeasTreatTables.rda")

Measurements %>% 
  left_join (Treatments) %>%
  mutate (when=ifelse(date>treatment_date,"after","before")) %>%
  spread(key=what,value=value) %>%
  select(subject,when,sbp,dbp,date)
```

