# Week 7 Short Answer Questions

## Your name should appear here!

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(lubridate)
```
<!-- put your content after this line -->

Here is my content!

##Problem 15.1

A. "April 30, 1777"

```{r}
mdy("August 30, 1995") - mdy("April 30, 1777") 
```

B. "06-23-1912"

```{r}
mdy("August 30, 1995") - mdy( "06-23-1912")
```

C. "3 March 1847"

```{r}
mdy("August 30, 1995") - dmy("3 March 1847") 
```

D. "11:00 am on Nov. 11th, 1918 at 11:00 am"

```{r}
 mdy("August 30, 1995") - 
```

E. "July 20, 1969"

```{r}
mdy("August 30, 1995") - mdy( "July 20, 1969")
```

##Problem 15.2

A. Here, as.numeric would not work because of the comma.  However, you can use extract_numeric() to change it into a numeric value.

B. In order to play around with this number, you should also use extract_numeric.

C. Cannot use either.

D. extract_numeric()

E. extract_numeric()

F. Here you can use etract_numeric(); however, this will include the squared part of the units.  You could use extract_numeric() and then write a loop that would run through the observations and delete the last number from each row.

G. This would not work for either unless you maybe used extract_numeric() and something else.

H. as.numeric()

I. as.numeric() {I think? Hard to tell because I don't know what it's actually supposed to be.}

#Chapter 16

##Problem 16.1

A.

```{r}
BabyNames_2 <-
  BabyNames %>%
  filter(sex == "M") %>%
  group_by(name) %>%
  summarise(total = sum(count)) 

BabyNames_3 <-
  BabyNames_2 %>%
  filter(grepl("[aeiou]$",name)) %>%
  mutate(rank = rank(desc(total)))

BabyNames_3 %>%
  filter(rank <= 10) %>%
  arrange(desc(rank))


```

B.

```{r}
BabyNames %>%
  group_by(name) %>%
  summarise(total = sum(count))%>%
  filter(grepl("joe|jo",name,ignore.case = T))
```
##Problem 16.2

These will match American phone numbers with area code. Only the numbers are being extracted.

##Problem 16.3

A. 2 characters

B. 62

C. The state you live in?



