# Week 6 Short Answer Questions

## Josh Marcus

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

##Chapter 12 Questions

#12.1

```{r}
Top5Names <- BabyNames %>%
  group_by(sex, name) %>%
  summarise(total=sum(count)) %>%
  filter(rank(desc(total)) <= 5)
```

```{r}
Top5Names
```

#12.2

```{r}
PopularCounts <- BabyNames %>%
  group_by(year, name) %>%
  summarise(total = sum(count))

PopularCounts <- PopularCounts %>% 
  mutate(frac_in_top_100 = rank(desc(total)))

PopularCounts$frac_in_top_100 <- ifelse(PopularCounts$frac_in_top_100 <=100 ,"True","False")
  
```

```{r}
GlyphReady <-
  PopularCounts %>%
  group_by(year, frac_in_top_100) %>%
  summarise(Total = sum(total)) %>%
  spread(frac_in_top_100, Total) %>%
  mutate(frac_in_top_100= `True` / (`True` + `False`))
```

```{r}
GlyphReady %>%
  ggplot(aes(x=year, y=frac_in_top_100)) +
  geom_line () +
  ylim(0,NA)
```

```{r}
GlyphReady
```

#12.3

a. summary
b. Neither. This operation makes a pair of values, whereas summary and transformation functions produce a single value.
c. summary
d. transformation
e. transformation
f. summary
g. transformation 
h. summary


##Chapter 13 Questions

#13.1

1. 8
2. 9

#13.2

1. A, B, C, D
2. Table 2
3. Table 1 says there's an edge between B and C, which is not true of the network, and it doesn't show the edge from C to D that's in the network. Table 3 has a third column, which isn't possible given the kind of 2D networks we're creating.

#13.3

Table 2

#13.4

1. Exports is mapped to the size of the letter.
2. Population is mapped to the shape of the symbol.

##Chapter 14 Questions

#14.1

```{r}
mosaicData::CPS85 %>%
  ggplot(aes(y = wage, x = sex)) +
  geom_boxplot(aes(fill=sex))
```

#14.3

For women, the most likely height is about 1.6 meters, and for men it's about 1.7 or 1.8 meters.

#14.7

```{r}
mosaicData::CPS85 %>%
  ggplot(y = wage, x = educ, color = sex) +
  geom_point() +
  stat_smooth(method="1m") +
  ylim(0,15)
```

#14.10

```{r}
mosaicData::Galton %>%
  ggplot(aes(x = height, group = sex)) +
  geom_density(aes(color = sex, fill = sex), alpha = 0.5) +
  xlab("height") + ylab("density")
```


