# Week 3 Project

---
title: "Playing with Frames, Glyphs, Scales"
output: html_notebook
---

## Becky Honnold

<!-- leave this material as is -->
Compiled on `r date()`.

```{r}
library(DataComputing)
library(mosaicData)
```

```{r}
#scatterGraphHelper(CPS85)
```


##Question 1

A. The first mode of graphic is a scatterplot that uses the variables sector, marital status, years of experience, and wage.
The second mode of graphic is a density plot that is looking at sex, bmi, and the 'yes', 'no' respresents pregnancy.

In the first plot, the sectors break the graphs up, the wage is the y-axis, the years of experience is the x-axis, and the color change represents the marital status.
In the second plot, the x-axis is BMI, theh color is sex, and the pregnancy indicator splits up the two graphs.

There is no data variable being used for the x-axis because the this is a density plot so the y-axis represents the density of the data.  

```{r}
ggplot(data = CPS85,aes(x = exper, y = wage, color = married)) + geom_point() + facet_wrap(~ sector) + xlim(0,20) + ylim(0,20)
       
ggplot(data = NCHS, aes(x = bmi)) + geom_density(aes(col = sex)) + facet_wrap(~pregnant)
```

##Question 2

```{r}
diamonds %>%
  group_by(color) %>%
  summarize(avg_Carat = mean(carat))
```

On average, it looks like the J color diamonds seem to be the largest on average.

##Question 3

```{r}
diamonds %>%
  group_by(clarity) %>%
  summarize(avg_table = mean(table))
```

On average, it looks like the I1 has the largest table per carat.

##Using Minneapolis2013 Data

##Question 1

```{r}
nrow(Minneapolis2013)
```

There are 80,101 cases.

##Question 2

```{r}
Second_Votes <-
  Minneapolis2013 %>%
  group_by(Second) %>%
  summarise(count  = n())

attach(Second_Votes)
Second_Votes <- Second_Votes[order(-count),]
```

The top 5 candidates in the Second vote selections were Betsy Hodges, Don Samuels, Mark Andrew, Jackie Cherryhomes, and Bob Fine.

##Question 3

```{r}
First_Choice <- 
  Minneapolis2013 %>%
  group_by(First) %>%
  summarise(count = n())


```

In the first choice selections, there were 834 undervotes.

```{r}
Second_Choice <- 
  Minneapolis2013 %>%
  group_by(Second) %>%
  summarise(count = n())
```

In the second choice selections, there were 10598 undervotes.

```{r}
Third_Choice <- 
  Minneapolis2013 %>%
  group_by(Third) %>%
  summarise(count = n())
```

In the third choice selections, there were 19210 undervotes.

##Question 4

```{r}
Question_4 <-
  Minneapolis2013 %>%
  group_by(First,Second) %>%
  summarise(count = n())
  
attach(Question_4)
Question_4_N <- Question_4[order(First, -count),]
```

Mark Andrew, Don Samuels, Jackie Cherryhomes

##Question 5

```{r}
Question_5 <-
  Minneapolis2013 %>%
  group_by(Precinct,First) %>%
  summarise(count = n(),avg = mean(First == "undervote"))

attach(Question_5)
Question_5_N <- Question_5[order(First,-count),]

```

P-02









