# Week 6 Short Answer Questions

## Becky Honnold

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(mosaicData)
```
<!-- put your content after this line -->

Here is my content!

##Chapter 12

###Problem 12.1

```{r}


BabyNames_F <-
  BabyNames %>%
  filter(sex == "F") %>%
  group_by(name) %>%
  summarise(count = sum(count)) %>%
  filter(rank(desc(count)) <= 5)

BabyNames_F

BabyNames_M <-
  BabyNames %>%
  filter(sex == "M") %>%
  group_by(name) %>%
  summarise(count = sum(count)) %>%
  filter(rank(desc(count)) <= 5)

BabyNames_M
  

```

###Problem 12.2

```{r}
Top_100 <-
  BabyNames %>%
  group_by(year) %>%
  filter(rank(desc(count)) <= 100) %>%
  summarise(total = sum(count)) %>%
  mutate(frac_in_top_100 = "TRUE")

Not_100 <-
  BabyNames %>%
  group_by(year) %>%
  filter(rank(desc(count)) > 100) %>%
  summarise(total = sum(count)) %>%
  mutate(frac_in_top_100 = "FALSE")  

merged_table <-
  Top_100 %>%
  full_join(Not_100) %>%
  arrange(year)

merged_table

GlyphReady <-
  merged_table %>%
  spread(frac_in_top_100,total) %>%
  mutate(frac_in_top_100 = `TRUE` / (`TRUE` + `FALSE`))

GlyphReady

ggplot(data=GlyphReady,aes(x=year,y=frac_in_top_100))+geom_point() 

```

###Problem 12.3

A. Transformation
B. Transformation
C. Summarize
D. Neither 
E. Neither
F. Summarize
G. Neither
H. Transformation

##Chapter 13

###Problem 13.1

1. 8
2. 9

###Problem 13.2

1. A, B, C, D
2. Table 2
3. They don't show the correct connections between the vertices.

###Problem 13.3

Table 2

###Problem 13.4

1. The number of exports is mapped to the size of the letter.
2. The population is mapped to the shape of the variable.

##Chapter 14

###Problem 14.1

```{r}
CPS85 %>%
  ggplot(aes(y = wage,x = sex)) + geom_boxplot(aes(color = sex,fill = sex))
```
###Problem 14.3

Based on the image, I would say that the most likely height for women is around 1.5 meters.  In contrast, I would estimate the most likely height for men is around 1.6m.

```{r}
NCHS %>%
  filter(sex == "female") %>%
  summarise(mean_height = mean(height,na.rm = T))

NCHS %>%
  filter(sex == "male") %>%
  summarise(mean_height = mean(height, na.rm = T))
```
###Problem 14.7

```{r}
ggplot(data=CPS85,aes(x=educ,y=wage))+geom_point()+aes(colour=sex) + stat_smooth(method=lm)
```

###Problem 14.10

```{r}
ggplot(data = Galton,aes(x = height, group = sex)) + geom_density(aes(color = sex))
```




