# Week 6 Short Answer Questions

## Xing Gao

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->


12.1
```{r}
BabyNames %>%
  group_by(name)%>%
  summarise(total=sum(count))%>%
  filter(rank(desc(total))<=5)
```
The top most popular names are James, John, Mary, Michael, and Robert, in this order

12.2

PopularCounts <- 
  BabyNames %>% 
  group_by(year,name) %>% 
  summarise(total = sum(count))%>% 
  mutate(frac_in_top_100 = rank(desc(total)) <= 100)  %>% 
  group_by(year, frac_in_top_100) %>% 
  summarise(total = sum(total))

GlyphReady <- 
  PopularCounts %>%
  spread(frac_in_top_100, total) %>%
  mutate(frac_in_top_100 = 'TRUE'/('TRUE'+'FALSE')) %>%
  ggplot(aes(x=year, y=frac_in_top_in100))

 
12.3
a. summary function
b. summary function
c. summary function 
d. transformation
e. transformation
f. summary
g. transformation
h. summary


13.1 
1. there are seven distinct vertices
2. there are 9 edges

13.2 
1. the vertices are A, B, C, D
2. Table 2 shows the edges correctly 

13.3
Table two gives the information to draw the graph correctly 

13.4
exports is mapped to the size of the letter
population is mapped to the shape of the gray symbol 

14.1
```{r}
CPS85 %>% 
  ggplot(aes(x=sex, y=wage))+geom_boxplot(aes(fill=sex))
```
14.3
the most likely height is about 1.7 for men, and 1.6 for women

14.7
```{r}
CPS85 %>%
  ggplot(aes(x=educ, y=wage, color= sex))+geom_point()+ylim(0,15)+stat_smooth(method= "lm")
```
14.10
```{r}
Galton %>%
  ggplot(aes(x=height, color=sex))+geom_density()
```