# Week 2 Project

## Phuc Nguyen 

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

```{r}
download.file("http://tiny.cc/dcf/Library-small.rda", dest = "Library-small.rda")
```

The data was downloaded from the link http://tiny.cc/dcf/Library-small.rda 

## Basics

```{r}
load("Library-small.rda")
```

```{r}
nrow(Inv)
names(Inv)
nrow(Bks)
names(Bks)
```

There are two data tables called Inv and Bks.
The library's collection is in Inv. Inv includes details about the books (i.e. author, title) and their library-related information (i.e. location, due date). Bks includes information of over 3000 books (i.e. genre, title) that may or may not be in the library's collection.

```{r}
library(dplyr)
Inv %>% group_by(Current.Status) %>% tally()
```

Most of the books are available! This library is really good at keeping track of their books since only 1 book is missing.

```{r}
Inv %>% group_by(Issued.Count) %>% tally()
```

Many books have never been checked out ... Around half of the books have never been checked out...


