# Week 2 Project

## Kai Heen 

Danny was here.

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

The data used in this document was provided by the Macalester College Library. It can be accessed at http://tiny.cc/dcf/Library-small.rda. 

#Basics

```{r}
load("Library-small.rda")
```

```{r}
dim(Inv)
dim(Bks)
```


```{r}
names(Inv)
names(Bks)
```


The Inv (Inventory) table has information about items in the Macalester College Library. There are 2000 items in this sample dataset, each with 18 variables. The variables describe the item (author, title, etc.) location of the item, and some of its checkout history. A complete list of these variables is shown above

The Bks (Books) table has information describing books that may or may not be in Macalester's Library. It has 3765 entries, each with 15 variables. The variables are all atributes of the books - a complete list of them is shown above. 


```{r}
Inv %>% group_by(Current.Status) %>% tally ()
```

```{r}
Inv %>% group_by(Issued.Count) %>% tally ()
```

The first chunk of code above groups the items in Macalester's collection by their current status. The above table tells us that 1866 of the items in this data set are available, and 115 are currently withdrawn.

The second chunk of code groups the books in Macalester's collection by the number of times they have been checked out. Thus, the above table tell us that the most popular amound of times for a item to be checked out is 0, followed by 2, 3, etc.