# Week 7 Short Answer Questions

## Qiuhan Sun

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

Here is my content!

## Problem 15.1
```{r}
library(lubridate)
lubridate::mdy("April 30, 1777") - lubridate::mdy("October 15th, 1996")
lubridate::mdy("06-23-1912") - lubridate::mdy("October 15th, 1996")
lubridate::dmy("3 March 1847") - lubridate::mdy("October 15th, 1996")
lubridate::mdy_hm("Nov. 11th, 1918 at 11:00 am") - lubridate::mdy_hm("October 15th, 1996 at 10:00 am")
lubridate::mdy("July 20, 1969") - lubridate::mdy("October 15th, 1996")

```

## Problem 15.2
#a 
tidyr::extract_numeric works

#b 
tidyr::extract_numeric works

#c 
none works

#d 
tidyr::extract_numeric works

#e 
none works

#f 
tidyr::extract_numeric works

#g 
none works

#h 
as.numeric works 

#i 
tidyr::extract_numeric works

## Problem 16.1
#1
```{r warning=FALSE}
BabyNames %>%
  group_by(name) %>%
  filter(sex == "M") %>%
  summarise(total = sum(count)) %>%
  filter(grepl("[aeiou]$", name)) %>%
  arrange(desc(total)) %>% 
  head(10)
```

#2
```{r}
BabyNames %>%
  group_by(name) %>%
  summarise(total = sum(count)) %>%
  filter(grepl("jo$|joe$", name)) %>%
  arrange(desc(total)) %>% 
  head(10)
```

## Problem 16.2
It's a phone number. 

[2-9] We are extracting 1 number from 2-9.

[0-9]{2} We are extracting 2 consecutive numbers from 0-9.

[- .] A dash, space or period

[0-9]{3} We are extracting 3 consecutive numbers from 0-9.

[0-9]{4} We are extracting 4 consecutive numbers from 0-9.

So we are getting a phone number, starting with 1 number from 2-9, two numbers from 0-9, a dash/space/period, three numbers from 0-9, a dash, then four numbers from 0-9.

## Problem 16.3
#1
The string will consist of two letters, such as AL, AK, AS.

#2
7 strings are matched for A[LKSZRAP]. 3 strings are matched for C[AOT]. In total, there are 61 strings.

#3.
These are abbreviations for U.S. states.

