# Week 3 Project

## Eloa

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(mosaicData)
```
<!-- put your content after this line -->
## In class notes

- Data verbs -> input = data tables, output = data tables
- Reduction verbs -> input = variables, single number/measure
- Transformation verv -> input = variable, output = new variable

6- data verbs:
deeplyedR?
1. summarise() -> allows to take datatable and reduce to single case
2. group_by() -> tell the systems to do other operations by given groups
3. filter() -> select out certain cases
4. mutate() -> apply a transformation verb
5. select() -> select certain variables that are of interested to you
6. arrange() -> re-order things 
7. join

## In Class 

Graph 1:
```{r}

ggplot(data=CPS85,aes(x=exper,y=wage)) +
  geom_point()+aes(colour=married) +
  scale_y_log10() +
  scale_x_log10() +
  facet_wrap(~sector) 
```

Graph 2:
```{r}

ggplot(data=NCHS,aes(x=bmi)) +
  geom_density(aes(colour=sex)) +
  facet_wrap(~smoker) 
```

Diamonds:
1.
```{r}
diamonds %>%
  group_by(color) %>%
  summarise(mean(carat)) %>%
  arrange(desc(`mean(carat)`)) %>% 
  head(1)

```

```{r}
diamonds %>%
  group_by(clarity) %>%
  summarise(mean(table/carat)) %>%
  arrange(desc(`mean(table/carat)`)) %>% 
  head(1)

```


Minneapolis
1-
```{r}
nrow(Minneapolis2013)
```
2-
```{r}
Minneapolis2013 %>%
  group_by(Second) %>%
  tally() %>%
  arrange(desc(n)) %>% 
  head(5)

```
3-
```{r}
Minneapolis2013 %>%
  filter(First == "undervote")%>%
  tally() %>%
  arrange(desc(n)) %>% 
  head(1)


Minneapolis2013 %>%
  filter(Second == "undervote")%>%
  tally() %>%
  arrange(desc(n)) %>% 
  head(1)

Minneapolis2013 %>%
  filter(Third == "undervote")%>%
  tally() %>%
  arrange(desc(n)) %>% 
  head(1)
```



4 - 
```{r}
Minneapolis2013 %>%
  filter(First == "BETSY HODGES")%>%
  group_by(Second) %>%
  tally() %>%
  arrange(desc(n)) %>% 
  head(3)

```

5-
```{r}
Minneapolis2013 %>%
  
  group_by(Precinct) %>%
  summarise(mean(First == "undervote")) %>%
  
  arrange(desc(`mean(First == "undervote")`))%>%
  head(1)

```
