# Week 4 Short Answer Questions

## Daniel Ochoa

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

Problem 8.1:
  a) 2
  b) 2
  c) 1
  d) 5
  e) 3
  f) 4
  g) 2
  h) 5

Problem 8.2:
# 1
```{r}
CPS85 %>%
  ggplot(aes(x = age, y = wage, shape = married)) + geom_point() + facet_wrap(~sector)
```

# 2
```{r}
CPS85%>%
  ggplot(aes(x=age, y=wage)) + geom_point() + facet_grid(sex~married)
```

Problem 8.3:
# A
```{r}
CPS85 %>%
  ggplot(aes(x=age, y=wage)) + geom_point()
```

# B
```{r}

CPS85%>%
  ggplot(aes(x = age, y = wage, shape = sex)) + geom_point()

```

# C
```{r}

CPS85%>%
  ggplot(aes(x = age, y = wage, shape = sex)) + geom_point() + facet_grid(married~.)

```

# D
```{r}
CPS85 %>%
  ggplot(aes(x = age, y = wage, shape = married)) + geom_point()
```


Problem 9.1: 
It seems like most of these are Data verbs, at least according to my notes and the handout. Yet within being a data verd there can specific other types of verbs like summary is also a summary verb? This confuses me a bit.
  a) Quick Presentation
  b) Data
  c) Transformation
  d) Summary
  e) Comparison
  f) Quick presentation
  g) Summary
  h) Data
  i) Quick Presentation


Problem 9.3:
1. The color J
2. The carat denoted by I1.
