# Week 3 Short Answer Questions

## Sam Erickson

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

5.1, 

```{r}
ggplot(data=CPS85,aes(x=sex,y=wage ,fill=married))+geom_bar(stat='identity',position='dodge', width=.9)+ facet_wrap(~race,ncol=3)
```

5.2

```{r}
HappinessIndex %>%
  WorldMap(key="country",fill="corruption")
```

6.5,
b.

6.6,
d. 

6.7,
d.

6.8

```{r}
Small <- NCHS %>%
  sample_n(size=5000)

ggplot(data=Small,aes(x=bmi,y=weight))+geom_point()+aes(colour=smoker)
```

Smoking status is mapped to color, bmi is matched to the x axis, weight is matched to y.


7.1,
a. summarise
b. mutate
c. arrange
d. filter
e. select
f. group_by + summarise

7.4,
a. No quotes are needed to identify the variable for grouping. Also, the BabyNames table has no variable called First.
b. You shouldn't list the data table in the argument for Tmp.
c. You forgot the %>% operator

```{r}
names(BabyNames)
BabyNames %>%
  group_by(sex) %>%
  summarize(votesReceived = n())
```
```{r}
Tmp <- group_by(BabyNames,year,sex) %>%
  summarise(totalBirths = sum(count))
```



7.5,
a. 
arrange(sex,desc(count))
b. 
filter(sex==F)
c.
filter(sex==M, count>=22)

d. 
filter(total=sum(count))
e.
select(name,count)


7.7,
a.
You only need to pass the data table name argument once.
```{r}
BabyNames %>%
  group_by(year,sex) %>%
  summarise(total=sum(count))
```

b.
No data table name argument is passed to tell what data to work with. ALSO NEED TO ACCOUNT FOR NA VALUES
```{r}
ZipGeography %>%
  group_by(State)%>%
  summarise(pop=sum(Population,na.rm=TRUE))
```

c. 
-> needs to be replaced with %>%
```{r}
Minneapolis2013 %>%
  group_by(First) %>%
  summarise(voteReceived = n())
```


d. 
%<% is not and operator. Neither is <-. The data table operator at the end needs to be placed at the front, and group_by needs to be done first.
```{r}
Minneapolis2013 %>%
  group_by(First) %>%
  summarise(votesReceived=n())
```



7.11,
a. sex, count, meanAge
b. diagnosis, count, meanAge
c. sex, diagnosis, count, meanAge
d. age, diagnosis, count, meanAge
e. age, count, meanAge

7.12
1. nrow()
2. names()
3. help()
4. library()
5. group_by
6. summarise()
