# Week 3 Project

## Danielle Niederkorn 

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

The first graph is a scatterplot. Along the x-axis is the experience of the workers, the y-axis contains the wages, the different colors represent the marital status of the workers, and the different graphs are split up by sector.

These variables allow comparisons between the different sectors, showing the relationship between wage and experience in different sectors. It also provides a visual cue as to societal expectations of workers in different sectors.

The second figure shows the density plot of the bmis of pregnant people. On the y-axis is the density, the x-axis shows the bmi, shades of pink represent females, blue represents males, and one graph shows the cases of pregnant vs non-pregnant people. The two graphs split up density vs bmi, and provide a seperate consideration for pregnant women. Since the plot is a density plot, instead of using a data variable, instead the density is calculated.

```{r}
ggplot(data = CPS85, aes(x = age, y = wage, color = sector)) + geom_point()
```


```{r}
ggplot(data = CPS85, aes(x = sector, y = wage, color = age)) + geom_point()

```


```{r}
ggplot(data = NCHS, aes(x = bmi)) + geom_density(aes(color = pregnant))

```
```{r}
diamonds %>%
group_by(color) %>%
summarise(mean(carat))


```
The D color diamonds have the highest average carats.

```{r}
 diamonds %>%
group_by(clarity) %>%
summarise(mean(table))


```
I1 has the largest average table per carat.


Minneapolis2013 has 80,101 cases. 

```{r}
Minneapolis2013 %>%
tally(x = Second)
```
1. Betsy Hodges 14399
2. Don Samuels 14170
3. Mark Andrew 12757
4. Jackie Cherryhomes 6470
5. Cam Winton and Bob Fine 3751

1. Undervote = 834

```{r}
Minneapolis2013 %>%
tally(x = First)
```

2. Undervote = 10598
```{r}
Minneapolis2013 %>%
tally(x = Second)
```

3. Undervote = 19210

```{r}
Minneapolis2013 %>%
tally(x = Third)
```

