# Week 4 Short Answer Questions

## MICHEALA SHAR P

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

#8.1 
###a. geom_point - adds a layer 
###b. geom_histogram - constructs the graphic frame 
###c. ggplot() - constructs the graphic 
###d. scale_y_log10()- changes the scale 
###e. ylab() - sets an axis label 
###f. facet_wrap constructs a new layer 
###g. geom_segment - ? 
###h. xlim() - sets the range for the s axis 
###i. ? 

#8.2 
##Graph 1 
```{r}
q <- CPS85 %>% 
ggplot(aes(x=age, y=wage))

q + geom_point(aes(shape=married)) + facet_grid(sector~.) + ylim(0,30) + xlim(0, 70)
```

##Graph 2
#**

#8.3 
##Graph A 
###creates a data frame and maps x to age and y to wage with points 
```{r}
Frame <- CPS85 %>% 
  ggplot(aes(x=age, y=wage)) 
  Frame + geom_point()
```
##Graph B 
###cant do B because corruption isnt apart of the CPS85 dataset 
##Graph C 
###wage on the y wage and x to age and two seperate frames for male and female
```{r} 
Frame <- CPS85 %>% 
  ggplot(aes(x=age, y=wage))
  Frame + geom_point(aes(shape=sex)) + 
  facet_grid (married~.)
```
##Graph D 
```{r}
Frame <- CPS85 %>% 
  ggplot(aes(x=age, y=wage)) 
  Frame + geom_point(aes(shape=married)) + 
  ylim(0,30)
```

#9.1 
###str() presentation 
###group_by() data verb 
###rank() transformation 
###mean() summary function 
###filter()data verb 
####merge() data verb 
###glimspe() quick presentation 

#9.3
##Part 1 
```{r}
diamonds%>% 
  group_by(color) %>% 
  summarise(size=mean(carat, na.rm =TRUE)) %>% 
  arrange(desc(size)) %>% 
  head(1)
```
##Part 2 
```{r}
diamonds%>% 
  group_by(clarity) %>% 
  summarise(ave_table = mean(table, na.rm= TRUE)) %>% 
  arrange(desc(ave_table)) %>% 
  head(1)
```
