# Week 3 Short Answer Questions

## Phuc Nguyen

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

##5.1
```{r}
library(mosaicData)
#barGraphHelper(CPS85)
```

##5.2
```{r}
HappinessIndex %>%
  WorldMap(key="country", fill="corruption")
```

##6.5
States and Polling Organizations

##6.6
d.

##6.7
d.

##6.8
```{r}
Small <- NCHS %>% sample_n(size=5000)
#scatterGraphHelper(Small)
```

bmi: x-axis
weight: y-axis
smoker: color

##7.1
a. mean()
b. mutate()
c. arrange(desc())
d. filter()
e. select()
f. group_by(), summarise(), max()

##7.4
a. group_by("First") -- remove quotation marks
b. summarise(Tmp, totalBirths = sum(count)) -- remove Tmp since this in a pipe
c. after group_by add '%>%'

##7.5
Table A: arrange(sex, count)
Table B: filter(sex == "F")
Table C: filter(sex == "M" & count >= 20)
Table D: summarise(total = sum(count))
Table E: select(name, count)

##7.7
a. BabyNames %>% group_by(year, sex) %>% summarise(total = sum(count))
b. ZipGeography %>% group_by(State) %>% summarise(pop = sum(Population))
c. Minneapolis2013 %>% group_by(First) %>% summarise(voteReceived = n())
d. Minneapolis2013 %>% group_by(First) %>% summarise(voteReceived = n())

##7.11
a. sex, count, meanAge
b. diagnosis, count, meanAge
c. sex, diagnosis, count, meanAge
d. age, diagnosis, count, meanAge
e. age, count, meanAge (the same as age)

##7.12
1. n()
2. names()
3. help()
4. library()
5. group_by()
6. summarise(sum())

