# Week 6 Short Answer Questions

## Katrin O'Grady

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

###Problem 12.1
```{r}
top5 <-
BabyNames %>%
  group_by(name) %>%
  filter(sex=="female") %>%
  summarise(total = sum(count)) %>%
  filter(rank(desc(total))<= 5)
```

###Problem 12.2
```{r}

```

```{r}
count_table <-
  BabyNames %>%
  group_by(year, name) %>%
  summarise(total_count= sum(count)) %>%
  mutate(frac_in_top_100 = rank(desc(total_count)))

```

```{r}
count_table$frac_in_top_100 <- ifelse(count_table$frac_in_top_100 <= 100,"TRUE","FALSE")
count_table <-
  count_table %>%
  group_by(year, frac_in_top_100) %>%
  summarise(total= sum(total_count))
```

```{r}
GlyphReady <-
  count_table %>%
  spread(frac_in_top_100, total) %>%
  mutate(frac_in_top_100 = `TRUE` / (`TRUE` + `FALSE`))
ggplot(GlyphReady, aes(x=year, y=frac_in_top_100)) + geom_line()
```

###Problem 12.3
a. summary
b. summary
c. summary
d. transformation
e. neither
f. transformation
g. neither
h. transformation

###Problem 13.1
1. There are 8 distinct vertices.
2. There are nine edges.

###Problem 13.2
1. The vertices are the shapes denoted with each letter- A, D, C, and B. 
2. Table 2 shows the edges correctly.
3. Table 1 lists as edge from B to C which is not shown in the diagram. Table 3 list an edge between three vertices, but an edge shows a connection between a pair of vertices. 

###Problem 13.3
Table 2 gives the information needed to draw the edges in the graph

###Problem 13.4
1. Exports is mapped to the size of the letter.
2. Population is mapped to the shape of the grey symbol. 

###Problem 14.1
```{r}
CPS85 %>%
ggplot(aes(y=wage, x=sex)) + geom_boxplot(aes(color= sex, fill=sex))
```

###Problem 14.3
Based on the graph, the most likely height for women is 1.6 and the most likely height fo men is 1.8.

###Proble 14.7
```{r}
CPS85 %>%
  ggplot(aes(y=wage, x=educ, color=sex)) + stat_smooth(method=lm) + geom_point(alpha=0.2)
```

###Problem 14.10
```{r}
Galton %>%
  ggplot(aes(x=height)) + geom_density(aes(fill=sex), alpha=0.5) + ylab("Density")
```

