# Week 4 Short Answer Questions

## Lang Li

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

```{r echo=FALSE}
options(warn=-1)
```

# Problem 8.1

(a) 2. Add a layer of glyphs.

(b) 2. Add a layer of glyphs.

(c) 1. Construct the graphics frame.

(d) 5. Change the scale for the facet.

(e) 3. Set an axis label.

(f) 4. Divide the frame into facet.

(g) 2. Add a layer of glyphs.

(h) 5. Change the scale for the frame.

(i) 4. Divide the frame into facet.

# Problem 8.2

The graph for fig 1
```{r}
ggplot(data=CPS85,aes(x=age,y=wage))+geom_point()+aes(shape=married)+facet_wrap(~sector,ncol=4) 

```

The graph for fig 2
```{r}
ggplot(data=CPS85,aes(x=age,y=wage))+geom_point()+facet_wrap(sex~married) 
```

# Problem 8.3

The graph a
```{r}
ggplot(data=CPS85,aes(x=age,y=wage))+geom_point()
```

The graph b

```{r}
HappinessIndex %>% WorldMap(key = "country", fill = "corruption")
```


The graph c
```{r}
ggplot(data=CPS85,aes(x=age,y=wage))+geom_point()+aes(shape=sex)+facet_grid(married~ . ) 
```

The graph d
```{r}
ggplot(data=CPS85,aes(x=age,y=wage))+geom_point()+aes(shape=married)
```

# Problem 9.1

(a) Quick presentation

(b) Data verb

(c) Transformation

(d) Summary function

(e) Data verb

(f) Quick presentation

(g) Data verb

(h) Data verb

(i) Quick presentation

# Problem 9.3

1.  J.
```{r}
diamonds %>% group_by(color,carat) %>% summarise(diam = mean(carat, na.rm = "True"))%>% arrange(desc(diam))%>% head(1)
```

2. I1
```{r}
diamonds %>% group_by(clarity) %>% summarise(diam1 = mean(table, na.rm = TRUE)) %>% arrange(desc(diam1)) %>% head(1)
```

