# Week 3 Short Answer Questions

## Yujin Jang

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

##5.1

Clean<-
  CPS85%>%
  group_by(sex)%>%
  summarise(total=n())
Clean1<-
  CPS85%>%
  group_by(race)%>%
  summarise(total=n())
barGraphHelper(Clean)

*I don't know why it wouldn't knit, so I just got rid of ```.


##5.2
```{r}
WorldMap(HappinessIndex,key="country",fill="corruption")
```

##6.5
b

##6.6
d

##6.7
d

##6.8

Small<-
  NCHS%>%
  sample_n(size=5000)
scatterGraphHelper(Small)

*I don't know why it wouldn't knit, so I just got rid of ```.

##7.1
a. mean(), b. c. 
##7.4
a. no "", 
b. you cannot us %>% like that get rid of it, 
c. you have to indent the second line.

##7.5
a. group_by (sex)
b.
c.
d.
e.

##7.7
a.
BabyNames %>%
  group_by(year, sex) %>%
  summarise(total=sum(count))
b.
ZipGeography %>%
  group_by(State) %>%
  summarise(pop=sum(Population))
c.
Minneapolis2013 %>%
  group_by(First) %>%
  summarise(voteReceived = n())
d.
Minneapolis2013 %>%
  group_by(First) %>%
  summarise(voteReceived = n())

##7.11
a.sex, count, meanAge
b.diagnosis, count, meanAge
c.sex, diagnosis, count, meanAge
d.age, diagnosis, count, meanAge
e.age, count, meanAge

##7.12
1.n()
2.
3.
4.library()
5.group_by()
6.