# Week 7 Project

## Kai Heen

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
Wake_county <- read.csv("http://tiny.cc/dcf/street-addresses.csv", stringsAsFactors = FALSE)
```

```{r}
pattern <- "ST|STREET|RD|ROAD|CIRCLE|WAY|TRAIL|WINERY|AVE|DR|LN|CIR|CT|LANE|POINT|PL|PLACE|COURT|PKWY|BLVD|PATH|LOOP|TERRACE|SQUARE|BLV"
LeftOvers <-
  Wake_county %>%
  filter( ! grepl(pattern, address),
          ! grepl(" BOX ", address)
  )
```


```{r}
pattern <- "(ST|STREET|RD|ROAD|CIRCLE|WAY|TRAIL|WINERY|AVE|DR|LN|CIR|CT|LANE|POINT|PL|PLACE|COURT|PKWY|BLVD|PATH|LOOP|TERRACE|SQUARE|BLV)"
  Wake_county %>%
    filter(!grepl("BOX ", address))%>%
    tidyr::extract(address, into = "street_word", 
          regex = pattern,
          remove = FALSE) %>%
    group_by(street_word) %>%
    summarise(total = n()) %>%
    arrange(desc(total))
```

The code above first filters out BOX addresses. It then uses tidyr::extract to create the new "street_word" variable. Finally, it groups by street word, and sums the total amount of occurances of each street word. By printing these in descending order, we can see the most popular street words. According to this data set, the most popular street keywords are Street, Drive, and Road.  
