# Week 4 Short Answer Questions

## Your name should appear here!

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

Here is my content!

8.1

a 2

b 2

c 1

d 5

e 3

f 4

g 2

h 1

i 2


8.2
```{r}
ggplot(data=CPS85,aes(x=age,y=wage, shape=married))+geom_point()+facet_wrap(~sector,ncol=3)+ylim(0,30)

```

```{r}

ggplot(data=CPS85,aes(x=age,y=wage))+geom_point()+facet_grid(married~sex)
```

8.3
```{r}
ggplot(data=CPS85,aes(age,wage))+geom_point()

```

```{r}
ggplot(data=CPS85,aes(age,wage,shape=sex))+geom_point()+facet_grid(married~.)

```

```{r}
ggplot(data=CPS85,aes(age,wage,shape=married))+geom_point()+ylim(0,30)

```

9.1

Data Verb,a Transformation,
Summary Function, or a Quick Presentation or a Comparison 
a) str() Quick Presentation

b) group_by() Transformation

c) rank() Comparison

d) mean() Summary

e) filter() Data Verb

f) summary() Quick presentation

g) summarise() Data Verb 

h) anti_join() Transformation

i) glimpse() Quick Presentation


9.3

```{r}
diamonds %>%
  group_by(color) %>%
  summarise(size=mean(carat)) %>%
  arrange(desc(size)) %>%
  head(1)
```

```{r}
diamonds %>%
  group_by(clarity) %>%
  summarise(size=mean(table)) %>%
  arrange(desc(size)) %>%
  head(1)
```
