# Week 4 Short Answer Questions

## Tristan Truttmann

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

### 8.1 

```{r include=FALSE}
library(ggplot2)
```

```{r}
Small <- BabyNames %>% sample_n(500)
Small %>%
  ggplot(aes(x = year, y = count)) +
  geom_point() + 
  xlab('Year Born') + 
  facet_wrap(~ sex) + 
  ylim(0,1000)
```

### 8.2

```{r include=FALSE}
library(mosaicData)
```

(1) 

```{r}
CPS85 %>%
  ggplot(aes(x=age,y=wage)) + 
  geom_point(aes(shape=married)) + 
  facet_wrap(~ sector) 
  
```

(2) 

```{r}
CPS85 %>%
  ggplot(aes(x=age,y=wage)) + 
  geom_point() + 
  facet_grid(sex ~ married)
```

### 8.3

(A) 

```{r}
CPS85 %>% 
  ggplot(aes(x=age,y=wage)) + 
  geom_point()
```

(B)

There exists neither a variable named "country" nor one named "corruption" in the CPS85 data table. 

(C) 

```{r}
CPS85 %>% 
  ggplot(aes(x=age,y=wage)) + 
  geom_point(aes(shape=sex)) + 
  facet_grid( married ~ . )
```

(D)

```{r}
CPS85 %>% 
  ggplot(aes(x=age,y=wage)) + 
  geom_point(aes(shape=married)) 
```

### 9.1

(a) A reduciton berb
(b) Data verb
(c) Transformation verb? I don't know what it means by rank. 
(d) Reduction Verb
(e) Data verb
(f) Reduciton verb
(g) Data verb
(h) Data verb
(i) Reduction verb

### 9.3

(1) 

```{r}
diamonds %>%
  group_by(color) %>% 
  summarize(AveSize = mean(carat)) %>% 
  arrange(-AveSize)
```

Based on this result, we see that color J is the largest on average.  J represents the worst quality of color.  

(2) 

```{r}
diamonds %>%
  group_by(clarity) %>%
  mutate(TpC = table/carat) %>%
  summarize(TpCAve = mean(TpC)) %>%
  arrange(-TpCAve) %>% 
  head(1)
```

Well the clarity VVS1 has the highest average table per carat. 


