# Week 3 Project

## Tristan Truttmann

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(ggplot2)
```
<!-- put your content after this line -->

(1) The first is a scatter plot, the second is a density plot. 
(2) The variables wage, exper, sector and married are involved for the first.  The variables bmi, sex, and pregnant are involved in the second. 
(3) In Figure 1, the variable `wage` is the y position.  Variable `exper` is the x coordinate of the points. Variable `sector` is indicated by which facet the points are in.  Variable `married` dictates the colors of the points.  In Figure 2, the density of `bmi` dictates the y values of the distribution glyphs.  `sex` dictates the colors of the distribution plots.  `pregnent` dictates which fasset the density is put in.  
(4)  There are not data variables on the y-axis because the y values are being used to represent the *density* of the `bmi` variable.  

### Graphing things: 

```{r}
CPS85 %>%
  ggplot() + 
  geom_point(aes(x=exper,y=wage,color = married)) + 
  facet_wrap(~ sector) +
  scale_y_log10()
```

```{r}
NCHS %>% 
  ggplot(aes(x=bmi)) + 
  geom_density(aes(fill=sex,alpha=0.8)) + 
  facet_grid(pregnant ~ . )
```

### Wrangling Diamonds! 

(1) 

```{r}
diamonds %>% 
  group_by(color) %>% 
  summarise(AveSize = mean(carat))
```

Color J has the largest average size in carats.  J just means that it is the lowerst quality color.  

(2) 

```{r}
diamonds %>% 
  mutate(TperC = table / carat) %>% 
  group_by(clarity) %>% 
  summarise(aveTperC = mean(TperC)) %>% 
  arrange(desc(aveTperC))
```

The VVS1 clarity has the largest everage "Table" per carat.  

### Wrangling Votes! 

```{r}
nrow(Minneapolis2013)
```

(1) There are 80101 cases. 

(2) 

```{r}
 Minneapolis2013 %>% 
  group_by(Second) %>% 
  summarize(votes = n()) %>% 
  arrange(desc(votes))
```

The top 5 candidates of second votes were Betsy Hodges, Don Samuels, Mark Andrew, Jackie Cherryhomes, and Bob fine tied with Cam Winton.  

(3) 

```{r}
Minneapolis2013 %>% 
  filter(First == "undervote") %>% 
  tally()
Minneapolis2013 %>% 
  filter(Second == "undervote") %>% 
  tally()
Minneapolis2013 %>% 
  filter(Third == "undervote") %>% 
  tally()
```

There were 834 "undervote" `First` choice selections, 10598 "undervote" `Second` choice selections, and 19210 "undervote" `Third` choice slections.  

(4) 

```{r}
Minneapolis2013 %>% 
  filter(First == "BETSY HODGES") %>% 
  group_by(Second) %>% 
  summarise(SecondVotes = n()) %>% 
  arrange(desc(SecondVotes)) %>% head(3)
```

The top 3 `Second` vote selections among voters who voted for Betsy Hodges as their first choice were Mark Andrew, Don Samuels, and Jackie Cherryhomes. 

(5) 

```{r}
Minneapolis2013 %>% 
  group_by(Precinct) %>% 
  summarize(total = n(),FirstUV = sum(First=="undervote")) %>% 
  mutate(ratio = FirstUV/total) %>%
  arrange(desc(ratio))
```

It seams that Precinct P-6C has the highest fraction.  7.7% of the votes had their `First` vote selections markes as "undervote". 



