# Week 7 Short Answer Questions

## Tristan Truttmann

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->


### 15.1 

```{r}
library(lubridate)
tristan <- ymd("1995-08-14")
gauss <- mdy("April 30, 1777")
tristan-gauss
turing <- mdy("06-23-1912")
tristan-turing
bell <- dmy("3 March 1847")
tristan-bell
arm <- parse_date_time("11:00 am on Nov. 11th, 1918",orders="H:M%m%d%y")
tristan - arm
moon <- mdy("July 20, 1969")
```
### 15.2

```{r}
library(tidyr)
as.numeric("42,659.30")
extract_numeric( "42,659.30")
as.numeric("17%")
extract_numeric("17%")
as.numeric("Nineteen")
extract_numeric("Nineteen")
as.numeric("£100")
extract_numeric("£100")
as.numeric("9.8 m/seconds-square")
tidyr::extract_numeric("9.8 m/seconds-square")
as.numeric("9.8 m/sˆ2")
extract_numeric("9.8 m/sˆ2")
as.numeric("6.62606957 × 10ˆ-34 m2 kg / s")
extract_numeric("6.62606957 × 10ˆ-34 m2 kg / s")
as.numeric("6.62606957e-34")
extract_numeric("6.62606957e-34")
as.numeric("42.659,30")
extract_numeric("42.659,30")
```

(a) Only `extract_numeric()` works. 
(b) None of these really work becuase they fail to interpret the percent sign correctly.  But `extract_numeric()` at least got the 17 part right. 
(c) They both fail on this one suprisingly. 
(d) Only the `extract_numeric` worked for this. 
(e) Wow they both fail here. 
(f) Only the `tidyr` function worked here. 
(g) Neither function worked here. 
(h) Hey! The as.numeric() function worked here! `extract_numeric()` did not work. 
(i) Only `extract_numeric()` worked here. 

### 16.1

(1) 

```{r}
library(DataComputing)
MaleWithVowel <- BabyNames %>%
  filter(sex=="M") %>% 
  filter(grepl("[aeiou]$",name)) %>% 
  group_by(name) %>%
  summarize(count = sum(count)) %>% 
  arrange(desc(count)) %>%
  head(10)
```
(2) 

```{r}
library(DataComputing)
EndWithJo <- BabyNames %>%
  filter(grepl("jo$|joe$",name)) %>% 
  group_by(name) %>%
  summarize(count = sum(count)) %>% 
  arrange(desc(count)) %>%
  head(10)
```

### 16.2

This regular expression would match any phone number that does not include parantheses in it and has 7 digits with the standars ., -, or space seperating the first 3 and the last 4 from the rest.  

### 16.3

(1) It will only be two characers. 
(2) It matches 61 characters. 
(3) This must be state abbreviations. (I'm not sure why there are 61, but I still think it is state abbreviations. )
