# Week 2 Project

##Micheala Sharp

<!-- leave this material as is -->
Compiled on `r date()`.
```{r}

```

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

##Basic
###The data was grabbed from online http://tiny.cc/dcf/Library-small.rda
```{r} 
load("Library-small.rda")
```

###The amount of rows in Inv and Bks 
```{r}
InvCases<-nrow(Inv)
InvCases
BksCases<-nrow(Bks)
BksCases
```
###The names of variables in Inv and Bks 
``` {r}
InvVars<-ls(Inv)
InvVars
BksVars<-ls(Bks)
BksVars
``` 
###What does it mean? 
*In Inv every case represents the location and identification of each book in the Macalester Library*
*In the Bks case each case represensents a specific book*

###More Fun Things 

```{r}
Inv %>% group_by(Current.Status) %>% tally()
```

*This chunk gives the variable Current.Status there are four different catagories Available, Missing, On Loan, or Withdrawn and the amount of books that corresponds to each catagory* 

```{r}
Inv %>% group_by(Issued.Count) %>% tally()
```
*This chunk tells you how many times a book has been issued*
