# Week 6 Short Answer Questions

## Yujin Jang

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

##12.1
```{r}
library(DataComputing)
BabyNames%>%
  group_by(sex,name)%>%
  summarise(total=sum(count))%>%
  filter(rank(desc(total))<=5)
```

##12.2

PopularCounts<-
  BabyNames%>%
  group_by(year)%>%
  summarise(total=sum(count))%>%
  group_by(frac_in_top_100)%>%
  filter(rank(desc(total))<=100)
  
GlyphReady<-
  PopularCounts %>%
  spread(frac_in_top_100, total)%>%
  mutate(frac_in_top_100=`TRUE`/(`TRUE`+`FALSE`))


##12.3
a.transformation 
b.transformation
c.summary
d.transformation
e.neither
f.summary 
g.transformation
h.transformation

##13.1
1. 8
2. 9

##13.2
1. A,B,C,D
2. Table 2
3. table 1: edge is not correctly combined, no B to C.
    table 3: It's connecting three vertices from A to C to D, which is not showing from to accurately.

##13.3
Table 2

##13.4
1. exports
2. pop

##14.1
```{r}
library(mosaicData)
CPS85%>%
  ggplot(aes(y=wage,x=sex))+
  geom_boxplot(aes(color=sex))
```


##14.3
male= 1.8
female= 1.6

##14.7
```{r}
CPS85%>%
  ggplot(aes(x=educ, y=wage , color=sex))+
  stat_smooth(method=lm)+
  geom_point()
```


##14.10
```{r}
Galton%>%
  ggplot(aes(x=height, group=sex))+
  geom_density(aes(color=sex, fill=sex, alpha=0.2))
```

