# Week 2 Project

## Danny Ochoa

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

I downloaded the data used in this program from "http://tiny.cc/dcf/Library-small.rda".

SECTION: BASICS

Calculating the number of cases in each file, Inv and Bks. 

The Inv file contains information on volumes in the library, their subject matter, their shelving location, call number and a few other variables.
```{r}
load("Library-small.rda")
tally(Inv)
```

The Bks file contains information about the subject of each book, its title, its author, its publication date, its publisher, and a few other varibales. 
```{r}
tally(Bks)
```


Looking at the number of books with each different Current.Status
```{r}
Inv %>%
  group_by(Current.Status) %>%
  tally()
```

Looking at how many times books have been checked out.
```{r}
Inv %>% 
  group_by(Issued.Count) %>%
  tally()
```

I believe this result means that there are 996 books in the data that been issued 0 times, 337 books that have been issued once, and so on.

