# Week 6 Short Answer Questions

##Wendy Chu

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

12.1
```{r}
BabyNames %>%
  group_by(sex, name) %>%
  summarise (allyear=sum(count)) %>%
  mutate(popularity=rank(desc(allyear))) %>%
  filter (popularity <= 5)
```


  
12.2
```{r}
PopularCounts <- 
  BabyNames %>% 
  group_by(year,name) %>% 
  summarise(total = sum(count))%>% 
  mutate(fractop100 = rank(desc(total)) <= 100)  %>% 
  group_by(year, fractop100) %>% 
  summarise(total = sum(total))
PopularCounts

```


Glyphr <- 
  PopularCounts %>% 
  spread(ranking, total) %>% 
  mutate(fractop100 = top_100 / (top_100 + notTop100))

Glyphr %>% 
ggplot(aes(x=year, y=fractop100)) + geom_line() + ylim(0, NA)


12.3
a. sum  b. neither  c. sum  d. tran e. tran f. sum  g. tran h. sum

13.1
there are 7 vertices: chn, frn, ger, itl, uk, usa, ussr
there are 9 edges

13.2
1. ABCD 2. table 2 3. there is no edge bc in t2, cannot have 3 edge in t3

13.3
table 2

13.4
1. exports 2. pop

14.1
```{r}
mosaicData::CPS85 %>%
  ggplot(aes(x=sex, y=wage)) + geom_boxplot(aes(fill=sex))
```

14.3
women ~1.6m, men ~1.75m

14.7
mosaicData::CPS85 %>%
  ggplot(aes(x=educ, y=wage, color=sex) + geom_point() + stat_smooth(method="lm") + ylim (0,5)

14.10
mosaicData::CPS85 %>%
  ggplot(aes(x=height, y=)) + geom_density(aes(color=sex))
