# Week 6 Short Answer Questions

## Qiuhan Sun

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

## Problem 12.1
```{r warning=FALSE}
BabyNames %>%
  group_by(sex, name) %>%
  summarise(count = sum(count)) %>%
  mutate(topfive = rank(desc(count))) %>%
  filter(topfive <= 5)
```

## Problem 12.2
```{r warning=FALSE}
Top100 <-
  BabyNames %>%
  group_by(year, name) %>%
  summarise(total = sum(count)) %>%
  mutate(top100 = ifelse(rank(desc(total)) <= 100, "True", "False" )) %>%
  group_by(year, top100) %>%
  summarise(total = sum(total))
Top100

GlyphReady <-
  Top100 %>%
  spread(top100, total) %>%
  mutate(frac_in_top_100 = True / (True + False))

GlyphReady %>%
  ggplot(aes(x=year, y=frac_in_top_100)) +
  geom_line() +
  ylim(0, NA)
```

## Problem 12.3
a. summary
b. neither; summary function only generates a single number
c. summary
d. transformation
e. transformation
f. summary
g. transformation
h. summary

## Problem 13.1
1.
There are 7 distinct vertices, including China, USSR, Germany, France, Italy, Japan, USA.
2.
There are 9 edges.

## Problem 13.2
1.
The vertices are A, B, C and D.
2.
Table 2 shows the edges correctly.
3.
Table 1 shows that there's a relationship between B and C, which does not exist.
The edges are relationship between pairs of vertices, but Table 3 shows three objects in a row,

## Problem 13.3
Table2

## Problem 13.4
1.
exports
2.
population

## Problem 14.1
```{r}
library(mosaicData)
CPS85 %>%
  ggplot(aes(x = sex, y = wage)) +
  geom_boxplot(aes(fill=sex))
```

## Problem 14.3
The most likely height for women is about 1.6 meters while for men is about 1.75 meters.

## Problem 14.7
```{r}
CPS85 %>%
  ggplot(aes(x = educ, y = wage, color = sex)) +
  geom_point() +
  stat_smooth(method="lm") 
```

## Problem 14.10
```{r}
Galton %>%
     ggplot(aes(x=height)) +
     geom_density(aes(fill=sex,color=sex), alpha=0.5)
```

