# Week 3 Short Answer Questions

## Tristan Truttmann

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

### 5.1

```{r}
library(mosaicData)
library(DataComputing)
ggplot(data=CPS85,aes(x=sex,y=wage ,fill=married))+geom_bar(stat='identity',position='dodge', width=.9)+scale_fill_brewer(type='qual',palette=1)+ facet_wrap(~race,ncol=3) 
```

### 5.2

```{r}
HappinessIndex %>% WorldMap(key="country",fill="corruption")
```

### 6.5

(a) Probability is represended by color and by the percentage strings.  State is represented by y position. 
(b) State is represented by y and poling organization is represented by x. 
(c) Domograts are represented by shades of blue and Republicans are represented by shades of Red. 
(d) State is represended b y y. 
(e) Probability is represented by color and by the strings in the boxes. 

### 6.6

I don't understand the question. 

### 6.7 

(d) NYT poll probability for the Democratic candidate. 

### 6.8 

```{r}
Small <- NCHS %>% sample_n(size=500)
ggplot(data=Small,aes(x=bmi,y=weight))+geom_point()+aes(colour=smoker)
```

* x is mapped to bmi
* y is mapped to weight
* color is mapped to smoker

### 7.1 

(a) This is the data verb `summarize()` 
(b) This is the `mutate()` verb
(c) This is the `arrang()` verb
(d) This is the `filter()` data verb
(e) This is the `select()` data verb
(f) This can be done with the `summarize()` data verb. 
 
 ### 7.4
 
 (a) There is not variable named `votesReceived` in the data table `BabyNames`.  
 (b) There is a redundancey.  Tmp is already piped throught the chain syntax, but then it is also included as the first argument in the `summarize()` function. 
 (c) Well it seams that the code is not doing what the use intended.  She defines Tmp, but then she uses summarize on the table `BabyNames`, but ruins the point of defining `Tmp` in the first placve. 

### 7.5 

(a) They seam to have done the operation `TableGiven %>% arrange(count) %>% filter(sex='F')` 
(b) She seams to have done the command `TableGiven %>% filter(sex='F')`
(c) She sheams to have done the operation `TableGiven %>% filter(sex='M',year<1980)`
(d) She seams to have done `TableGiven %>% summarize(total=n())`
(e) She seams to have run the command `TableGiven %>% select(name,count)

### 7.7 

(a) BabyNames should not be included as the first argument if the chain syntax is being used. 
(b) There is not data table listed for the functions to act on. 
(c) Once agian the user is using the assugment operator where she should be using the chain syntax operator. 
(d) I have not clue what this person is trying to do, but you can't assign a called function with a varaible.  

### 7.11

(a) The output will show the number of patients of each sex and the mean age of the males and females that were patients. 
(b) The output will show the number of each kind of diagnosis, and the mean age of those diagnoses. 
(c) This will show the number of patients iwth each sex-diagnosis combination, and it will show the average age for each of those combinaitons. 
(d) This will show the number of patients with each age-diagnosis combination, and it will show the average age, which is kind of redundant. 
(e) This will show the number of patients at each age, and it will show the age again.  

### 7.12

(1) `n()`
(2) `colnames()`
(3) `help()`
(4) `libarary()`
(5) `group_by()`
(6) `DataTable %>% sumarize(HowMany = sum(variable))'
 
