# Week 3 Project

## Danny Ochoa

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(ggplot2)
```
<!-- put your content after this line -->

Diamonds
Problem 1.
```{r}
diamonds %>%
  group_by(color) %>%
  summarise(ave = mean(carat)) %>%
  arrange(desc(ave)) %>%
  head(1)
```

The color denoted by 'J' seems to be the largest on average (in terms of carats). It's average size is 1.1621368 carats.

Problem 2.
```{r}
diamonds %>%
  group_by(clarity) %>%
  summarise(ave = mean(table)) %>%
  arrange(desc(ave)) %>%
  head(1)

```

The clarity denoted by 'I1' seems to be the largest on average (in terms of table). It's average size is 58.30378.


Voting
Problem 1.
```{r}
x <- Minneapolis2013 %>% tally()
```

There are `r x`

Problem 2.
```{r}
Minneapolis2013 %>%
  group_by(Second) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  head(5)
```

The top 5 second voting candidates is Betsy Hodges, Don Samuels, Mark Andrew, undervote, Jackie CherryHomes.

Problem 3.
```{r}
Minneapolis2013 %>%
  filter(First == "undervote") %>%
  tally()
```

There were 834 votes marked undervote in the first ballot.

```{r}
Minneapolis2013 %>%
  filter(Second == "undervote") %>%
  tally()
```

There were 10598 votes marked undervote in the second ballot.

```{r}
t <- Minneapolis2013 %>%
  filter(Third == "undervote") %>%
  tally()
```

There were `r t` votes marked undervote in the third ballot.

Problem 4.
```{r}
Minneapolis2013 %>%
  filter(First == "BETSY HODGES") %>%
  group_by(Second) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  head(3)
```

The top 3 second vote selections among people who voted for Betsy Hodges as their first choice are Mark Andrew, Don Samuels, and Jackie Cherryhomes in that order.

Problem 5.
```{r}
Minneapolis2013 %>%
  group_by(Precinct) %>%
  summarise(ave = mean(First == "undervote")) %>%
  arrange(desc(ave)) %>%
  head(1)
```

Precinct P-6C had 0.07738095% of it's First votes casted as "undervote", this was the highest fraction. 