# Week 7 Short Answer Questions

## Joseph Goodson-Gregg

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

Chapter 15 Questions: (15.1, 15.2)

15.1

a.) ”April 30, 1777"
mdy(”April 30, 1777”)

b.) ”06-23-1912"
mdy(”06-23-1912”)

c.) ”3 March 1847"
dmy(”3 March 1847”)

d.) ”11:00 am on Nov. 11th, 1918 at 11:00 am"
mdy_hm("11:00 am on Nov. 11th, 1918 at 11:00 am") #This did not work

e.) ”July 20, 1969"
mdy(”July 20, 1969”)






15.2

Generally it makes sense to use as.numeric() with the input is in number format, but identified as a different type of data. eg "25". as.numeric("25") will output the number 25. tidyr::extract_numeric() makes sense when there is punctuation to deal with.

a.) "42,659.30"

as.numeric("42,659.30") #does not work
tidyr::extract_numeric("42,659.30") #works

b.) "17%"
as.numeric("17%") #does not work
tidyr::extract_numeric("17%") #works, returns 17 not .17 though, good to note

c.) "Nineteen"
as.numeric("Nineteen") #does not work
tidyr::extract_numeric("Nineteen") #does not work

d.) "£100"
as.numeric("£100") #does not work
tidyr::extract_numeric("£100") #returns 100

e.) "9.8 m/seconds-square" 
as.numeric("9.8 m/seconds-square") # does not work.
tidyr::extract_numeric("9.8 m/seconds-square") #did not work, unsure why

f.) "9.8 m/sˆ2"
as.numeric("9.8 m/sˆ2") #did not work
tidyr::extract_numeric("9.8 m/sˆ2") #worked, returned 9.8

g.) "6.62606957 Å~ 10ˆ-34 m2 kg / s"
as.numeric("6.62606957 * 10^-34 m2 kg / s") #does not work
tidyr::extract_numeric("6.62606957 * 10^-34 m2 kg / s") #does not work

h.) "6.62606957e-34"
as.numeric("6.62606957e-34") #e is a number, returned a number, valid format!
tidyr::extract_numeric("6.62606957e-34") #Interestingly, did not work.

i.) "42.659,30" (A European style)
as.numeric("42.659,30") #did not work
tidyr::extract_numeric("42.659,30") #'worked', but returned 42.659.




Chapter 16 Questions: (16.1, 16.2, 16.3)

16.1

```{r}
pattern <- "[aeiou]$"
BoyNamesVowel <-
  BabyNames %>%
  filter(grepl(pattern, name)) %>%
  filter(sex == "M") %>%
  group_by(name) %>%
  summarise(total = n()) %>%
  arrange(desc(total))
BoyNamesVowel %>%
  head(10)
```

2.

```{r}
pattern <- "(joe|jo)$"
NamesWithJo <-
  BabyNames %>%
  filter(grepl(pattern, name)) %>%
  group_by(name) %>%
  summarise(total = n()) %>%
  arrange(desc(total))
NamesWithJo %>%
  head(10)
```


16.2

"([2-9][0-9]{2})[- .]([0-9]{3})[- .]([0-9]{4})"
number 2-9 then another number 0-9. Then either a space period or dash. Then three numbers in a row that are between 0 and 9, then either a space period or dash, finally four more numbers consecutively between 0 and 9.
This is the format of a telephone number. eg.
319-541-9809


16.3

Consider this regex:
(A[LKSZRAP]|C[AOT]|D[EC]|F[LM]|G[AU]|HI|I[ADLN]|
K[SY]|LA|M[ADEHINOPST]|N[CDEHJMVY]|O[HKR]|P[ARW]|
RI|S[CD]|T[NX]|UT|V[AIT]|W[AIVY])
(Ignore the line breaks)
1. How long will the strings be that match the pattern?
Two characters.
2. How many different strings will match?
7+3+2+2+2+1+4+2+1+10+8+3+3+1+2+2+1+3+4=68
3. People living in the United States may be able to figure out what the pattern is meant to express. Give it a try.
I assume these are state abbreviations. It is a list of accepted states, and perhaps a few territories. I see that PR (Puerto Rico) is included, as is PW (Palau).