# Week 7 Short Answer Questions

## Sam Erickson

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

15.1

```{r}
library(lubridate)
myBirthday = "December 16, 1994"
myBirthday = mdy(myBirthday)
str1 = "April 30, 1777"
str2 = "06-23-1912"
str3 = "3 March 1847"
str4 = "Nov. 11th, 1918 at 11:00 AM" # HOW THIS??
str5 = "July 20, 1969"
date1 = mdy(str1)
date2 = mdy(str2)

gauss = as.Date(myBirthday) - date1
turing = myBirthday - date2
bell = myBirthday - dmy(str3)
wwi = as.POSIXct(myBirthday) - mdy_hm(str4)
moonLanding = myBirthday - mdy(str5)
```


15.2

```{r}
a = "42,659.30"
b = "17%"
c = "Nineteen"
d = "$100"
e = "9.8 m/seconds-square"
f = "9.8 m/s^2"
g = "6.62606957 x 10^-34 m2 kg / s"
h = "6.62606957e-34"
i = "42.659,30"

list = c(a,b,c,d,e,f,g,h,i)
numbers = as.numeric(list)
numbers
numbers2 = tidyr::extract_numeric(list)
numbers2
```
The as.numeric() function only worked for "6.62606957e-34".

tidyr::extract_numeric() worked for everything except "Nineteen", "9.8 m/seconds-square", "6.62606957 x 10^-34 m2 kg / s","6.62606957e-34", and it added an extra 0.02 to  "9.8 m/s^2" for some reason'



16.1, 

```{r}
BabyNames %>%
  filter(sex=="M") %>%
  group_by(name) %>%
  filter(grepl("[aeiou]$",name)) %>%
  summarise(Total = sum(count)) %>%
  arrange(desc(Total)) %>%
  filter(rank(desc(Total))<=10)
```
```{r}
BabyNames %>%
  group_by(name) %>%
  filter(grepl("joe$|jo$",name)) %>%
  summarise(Total = sum(count)) %>%
  arrange(desc(Total)) %>%
  filter(rank(desc(Total))<=10)
```


16.2,
This expression would match an American phone number. 


16.3

1. Strings will be two characters long
2. About 52- 56 strings will match. I didn't count, but that's about the amount of states + territories
3. I think that these are all possible US state codes, including PR for puerto rico. 