`[iujioollplllp# Week 3 Project

## Josh Marcus

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

##Deconstructing Graphics

#Graphic 1
* This is a scatter plot.
* exper, wage, secot and married are involved
* exper is on the x axis. wage is on the y axis. The facet wrap is sector, and married maps marital status across two colors of points in the scatterplot.

#Graphic 2

* Graphic 2 is a density plot.
* bmi, pregnant, and sex are involved.
* bmi is on the x axis, pregnant is the faceet wrap, and sex maps its two categorical levels across the density plot. 
* There's no data variable being used on the y axis here because density is a function that's working on bmi, calculating the density of its various values across NCHS.

```{r}
ggplot(data = CPS85, aes(x = exper, y = wage, color = married)) + geom_point() + facet_wrap( ~ sector)
```

```{r}
ggplot(data = NCHS, aes(x = bmi)) + geom_density(aes(color = sex)) + facet_wrap(~ pregnant)
```

##Wrangling

#Diamonds

#1: Which color of diamonds seem to be largest on average (in terms of carat)?
```{r}
diamonds %>%
  group_by(color) %>%
  summarise(avgsize = mean(carat)) %>%
  arrange(desc( avgsize)) %>%
  head (1)
```

J diamonds seem to be largest on average in terms of carat.

#2: Which clarity of diamonds has the largest average "table" per carat?
```{r}
diamonds %>%
  group_by(clarity) %>%
  summarise(avgtable = mean(table)) %>%
  arrange(desc( avgtable)) %>%
  head (1)
```

I1 clarity seem to have the largest average table per carat.

#Voting

1. There are 80,101 cases in Minneapolis2013
2. Who were the top 5 candidates in the Second vote selections>

```{r}
X <- Minneapolis2013 %>%
  group_by (Second) %>%
  summarise(total=n()) %>%
  arrange(desc(total)) %>%
  head(6)
  
```

The top 5 were as follows: 
* Betsy Hodges
* Don Samuels
* Mark Andrews
* Jackie Cherryhomes
* Bob Fine

3. How many ballots are marked "undervote" in First, Second, and Third choice selections:

```{r}
FirstVotes <- Minneapolis2013 %>%
  filter (First == "undervote") %>%
  tally()
```
First: 834
```{r}
SecondVotes <- Minneapolis2013 %>%
  filter (Second == "undervote") %>%
  tally()
```
Second: 10598
```{r} 
ThirdVotes <- Minneapolis2013 %>%
  filter (Third == "undervote") %>%
  tally()
```

Third: 19210

4. What are the top 3 Second vote selections among people who voted for Betsy Hodges as their first choice?

```{r}
HodgesLovers <- Minneapolis2013 %>%
  filter (First == "BETSY HODGES") %>%
  group_by(Second) %>%
  tally() %>%
  arrange(desc(n)) %>%
  head( 3 )
```

Mark Andrews, Dawn Samuels, and Jackie Cherryholmes were the top 3 Second choices for people who voted Betsy Hodges.

5. Which precinct had the highest fraction of First vote selections marked as undervote?

```{r}
UnderVotes <- Minneapolis2013 %>%
  filter (First == "undervote") %>%
  group_by(Precinct) %>%
  tally () %>%
  arrange(desc(n))
```

P-02 had the most First selections marked undervote.
