# Week 4 Project

## Katrin O'Grady

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

###Problem 8.1
1. construct the graphics frame: c) ggplot()
2. add a layer of glyphs: a) geom_point(), g) geom_segment(), b) geom_histogram()
3. Set an axis label: e) ylab()
4. Divide the frame into facets: f) facet_wrap(), i) facet_grid()
5. CHange the scale for the frame: h) xlim(), d) scale_y_log10()
###Problem 8.2
```{r}
CPS85 %>%
ggplot(aes(x=age, y=wage, shape=married)) + geom_point() + facet_wrap(~sector)

```

```{r}
CPS85 %>%
ggplot(aes(x=age, y=wage)) + geom_point() + facet_grid(sex~married)
```

###Problem 8.3
```{r}
CPS85 %>%
ggplot(aes(x=age, y=wage)) + geom_point()

```

```{r}
CountryData %>%
WorldMap(key="country", fill="birth")
```

```{r}
CPS85 %>%
ggplot(aes(x=age, y=wage, shape=sex)) + geom_point() + facet_grid(married~.)
```

```{r}
CPS85 %>%
ggplot(aes(x=age, y=wage, shape=married)) + geom_point()
```
###Problem 9.1
a) str() is a summary function
b) group_by() is a data verb
c) rank() is a comparison expression
d) mean() is a reduction function
e) filter() is a data verb
f) summary() is a summary function
g) summarise() is a data verb
h) anti_join() is a comparison expression
i) glimpse() is a summary function

```{r}
diamonds %>%
group_by(color) %>%
summarise(size= mean(carat)) %>%
arrange(desc(size)) %>%
head(1)

```

```{r}
diamonds
group_by(clarity) %>%
mutate(table_carat= mean(table/carat) %>%
arrange(desc(table_carat)) %>%
head(1)

```


