# Week 3 Project

## Joseph Goodson-Gregg

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

Here is my content!

(1) The first graphic is a scatter plot. The second graphic is density plot.
(2) First graphic has wage, experience, marriage status, and type of worker. The second graphic has density, bmi, sex, pregnancy status.
(3) Wage and experience set the frame for the first graphic. The other variables define the aesthetics. Density and bmi define the frame, the other variables define the aesthetics.
(4) A density plot ranges from 0 to 1 with relative density. Since it is relative it is unitless.

```{r}
ggplot(data=CPS85,aes(x=exper,y=wage)) + 
  geom_point()+aes(colour=married)+
  scale_x_log10()+
  scale_y_log10()+
  facet_wrap(~sector,ncol=4) 
ggplot( data = NCHS, aes(x = bmi)) + geom_density(adjust=0.4) + aes(colour=sex) + facet_wrap(~pregnant, ncol=4) + labs(title="") + theme(legend.position="right") 
```

```{r}
diamonds %>% group_by(color, carat) %>% summarise(typical = mean(carat, na.rm = TRUE)) %>% arrange(desc(typical))

diamonds %>% group_by(clarity) %>%
    summarise(avgTypical = base::mean(table/carat)) %>%
    arrange(desc(avgTypical)) %>%
    head(1)
```

(1) The best quality diamonds (D) seem to be the largest.
(2) The clarity of diamond with the largest average table per carat was VVS1, with a dbl of 141.4822.

```{r}
Minneapolis2013 %>%
    group_by(First) %>%
    summarise(top5 = n()) %>%
    arrange(desc(top5)) %>%
    head(5)
    
Minneapolis2013 %>%
    group_by(First) %>%
    filter(First == "undervote") %>%
    summarise(firstchoice = n()) %>%
    head(1)

Minneapolis2013 %>%
    group_by(Second) %>%
    filter(Second == "undervote") %>%
    summarise(secondchoice = n()) %>%
    head(1)

Minneapolis2013 %>%
    group_by(Third) %>%
    filter(Third == "undervote") %>%
    summarise(thirdchoice = n()) %>%
    head(1)

Minneapolis2013 %>%
    group_by(First) %>%
    filter(First == "BETSY HODGES") %>%
    group_by(Second) %>%
    summarise(hodges = n()) %>%
    arrange(desc(hodges)) %>%
    head(3)
```


Voting
(1) 80,101 cases
(2) BETSY HODGES, MARK ANDREW, DON SAMUELS, CAM WINTON, JACKIE CHERRYHOMES.
(3) First choice: 834. Second choice: 10598. Third choice: 19210.
(4) MARK ANDREW, DON SAMUELS, JACKIE CHERRYHOMES.
(5) 

