# Week 3 Short Answer Questions

## Nana Adom Mills-Robertson

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

**5.1**

```{r}
library(mosaicData)
library(DataComputing)
ggplot(data=CPS85,aes(x=sex,y=wage ,fill=married))+geom_bar(stat='identity',position='dodge', width=.9)+ facet_wrap(~race,ncol=3)
```

**5.2**
```{r}
HappinessIndex%>%
WorldMap(key = "country", fill = "corruption")

```

**6.5**
b.

**6.6**
d.

**6.7**
a.

**6.8**
```{r}
Small <-NCHS %>%
  sample_n(size=5000)
```

scatterGraphHelper(Small)

ggplot(data=Small,aes(x=bmi,y=weight))+geom_point()+aes(colour=smoker) 


**7.1**
a. summarise

b. mutate

c. arrange

d. filter

e. select

f.group_by


**7.4**
a. group_by("First") is the error it should not be in quotation marks

b. tmp <- group_by.... is the error, no dataset was defined. BabyNames dataset was       within group_by which is flawed.
c. tmp <- group_by... is the error, no dataset defined, 

**7.5**
a. group_by(sex)
   arrange(count)

b. filter( sex != "M"")
   
c. filter ( sex != "F")

d. summarise (count = n())

e. group_by( name )
   summarise( total = sum(count))
   
   
**7.7**
a. BabyNames %>%
      group_by( year, sex) %>%
      summarise( count = n(),
                 total = sum(count))

b. ZipGeography %>%
      group_by(State) %>%
      summarise( pop = sum(Population))
      
c. Minneapolis2013 %>% 
    group_by(First) %>%
    summarise (voteReceived = n())
    
d. Minneapolis2013 %>%
    group_by(First) %>%
    summarise(votesReceived = n())
    
**7.11**

Patients %>% 
  group_by(**some variables) %>%
  summarise(count = n(), meanAge = mean(age))
  
a. sex, count, meanAge

b. diagnosis, count, meanAge

c. sex, diagnosis, count, meanAge

d. age, diagnosis, count, meanAge

e. age, count, meanAge

**7.12**

1. nrow()

2. ncol()

3. help()

4. library()

5. group_by

6. summarise()