# Week 5 Short Answer Questions

## Your name should appear here!

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

### 10.1

This is because two data tables are required as inputs to join family data verbs, while other data verbs only require one data table as input.

### 10.2

This cannot be done because the countries in these tables are not in the same order.

### 10.3

Table B would make it easiest to find difference between 2000 and 2001 for each contry. I'll just subtract Y2000 from Y2001 and put results in a new column

Table C would make it easiest to find sum of values for each continents for each year. The code to do this:

C %>% 
inner_join(ContinentData, by = Country) %>%
group_by(Year, Continent) %>%
sum(Value)

### 11.1

* Note: convert wide to narrow format using spread and gather in tidyr package

V.1: A name for each sex, each year ( either 2012 or 1912) and its count
V.2: A name for each year and count for each sex
V.3: A name for each sex and count for each year

V.1 is narrow and V.2 is wide
"key" variable is sex

Because there are no Harrison as a name for a female

Because V.2 separates sex into variables while V.3 separates year instead.

In spread, key is year, and value is nbabies

F and M were gathered. "key" variable sex appears in V. 1 

### 11.3
a. A is wide, C is narrow
b. B is wide, C is narrow

### 11.4

when          sbp
BHO-before     #
...           ...

### 11.5

```{r}
"http://tiny.cc/dcf/MeasTreatTables.rda" %>%
  url() %>% load()

```




