# Week 4 Short Answer Questions

## Joshua Doyle!

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

Here is my content!

##8.1

**a)** Geom_point(): Add a layer of glyphs 
**b)** Geom_Histogram(): Construct the Graphic Frame
**c)** GGplot(): Construct the Graphic Frame 
**d)** ScaleYLog10:Change the scale for the frame 
**e)** ylab: Set an axis label
**f)** facet wrap: Divide the frame into facets
**g)** geom_segment: Add a layer of glyphs
**h)** xlim: Change the scale for the frame
**i)** facet_grid: Divide the frame into facets

##8.2

**1:**

```{r}
ggplot(data = CPS85, aes(x = age, y = wage)) + 
  xlim(20,60) +
  ylim(0,30) +
  geom_point(aes(shape = married)) +
  facet_wrap(~ sector) 
 
```

**2:**

```{r}
ggplot(data = CPS85, aes(x = age, y = wage)) +
  geom_point() +
  facet_grid(sex ~ married)  
```


##8.3

**A)**

```{r}
ggplot(data = CPS85, aes(x = age, y = wage)) +
  geom_point()
```

**B)**

```{r}
WorldMap(HappinessIndex, key=country, fill=corruption)
```

**C)**

```{r}
ggplot(data = CPS85, aes(x = age, y = wage)) +
  geom_point(aes(shape = sex)) + 
  facet_grid(married ~ .)
```

**D)**

```{r}
ggplot(data = CPS85, aes(x = age, y = wage)) +
  geom_point(aes(shape = sex)) +
  ylim(0,30)
```

##9.1 

a) str(): Quick Presentation
b) group_by: Data verb
c) rank: Transformation
d) mean(): Summary Function
e) Filter(): Data Verb
f) Summarise(): Data Verb
h) Anti_join(): Transformation
i) Glimpse(): Quick Presentation

##9.3) 

**1)**

```{r}
diamonds %>%
  group_by(color) %>%
  summarise(Size = mean(carat)) %>%
  arrange(desc(Size)) %>%
  head(1)
```

**The diamond with color J has the largest average carat with 1.16.**

**2)**

```{r}
diamonds %>%
  group_by(clarity) %>%
  summarise(AvgTable = mean(table/carat)) %>%
  arrange(desc(AvgTable)) %>%
  head(1)
```

**VVS1 is the clarity with the higherst average table per carat. **

