# Week 5 Project

## Daniel Ochoa

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(ggplot2)
```
<!-- put your content after this line -->

Here I load my files
```{r}
load("ScorecardSmall.Rda")
NPT4convert <- read.csv("http://tiny.cc/dcf/NPT4-names.csv")
NPT4convert
```

Here I create my "narrow" data set called Economist, from the given "wider" dataset called ScorecardSmall.
I filter out the cases where CONTROL == 3 because these are not used in the Economist's graphic. I select the various variables that I am interested in. I then gather the data accordingly and join it with my csv file.
```{r}
Economist <-
  ScorecardSmall %>%
  filter(CONTROL != 3) %>%
  select(ADM_RATE, CONTROL, NPT41_PUB, NPT43_PUB, NPT45_PUB, NPT41_PRIV, NPT43_PRIV, NPT45_PRIV) %>%
  gather(key = long_name,Net_cost_per_year, -c(CONTROL, ADM_RATE)) %>%
  left_join(NPT4convert)
```

Here I use the Economist data set I just made to produce a plot. 
```{r}
ggplot(data=Economist, aes(x=ADM_RATE, y=Net_cost_per_year)) + geom_point() +facet_grid(CONTROL~short_name) + geom_smooth()
```

