# Week 5 Short Answer Questions

## Tristan Truttmann

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

### 10.1

Come on it's just because joining by definition takes two tables instead of one as arguments. 

### 10.2

This stratagie will not work becuase the `CountryCentroids` table must having mising countries as evidenced by the fact that it has 241 rows where the `Demographics` table has 256 rows.  

### 10.3

(1) I think that table B would be the easiest to calculate this becuase you would just use the `mutate()` data verb to add a new veriable by subtraticting `Y2000` from `Y2001`.  
(2) I think that Table B is once again best for this.  First I would left join Table B and `ContinentData` with Table B on the left.  Then I would use the `group_by()` function to sort them by continent, and the `summarize()` funciton to sum of all the counries in each continent.  

### 11.1

(a) In Version one, each case is a given name for a given sex on a given year.  For vresion two, each case is a given name in a given year.  In Version Three, each case is a given name.  

(b) Version One is narrrow, version two is wide. 

(c) The sex is teh key veriable.  

(d) The NA's in version Two and Three are represented by missing cases in Version One. 

(e) Version 3 contains fewer cases but contains more variables, so one case in Three represents multple cases in Two and One. 

(f) The `nbabies` variable was the `value` during the spread operation. 

(g) 

* The variables `F` and `M` were gathered into One.  
* The `sex` variable was created as the key variable. 
* The values `F` and `M` were taken from the variable names in Verson Two. 

### 11.3

(a) Table A is wide. Table B is narrow. 
(b) Table B is wide. Table C is narrow. 
(c) Table A is wide.  Table C is narrow. 

### 11.4

Okay I promise I did this.  

### 11.5 

(1) 

```{r}
"http://tiny.cc/dcf/MeasTreatTables.rda" %>%
  url() %>% load()

```

