# Week 2 Short Answer Questions

## Qiuhan Sun

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

Here is my content!

##Problem 1.1

a) Taffy. It’s the value of a variable for a particular case.
b) Year. It's a quantitative variable.
c) Sex. It's a categorical variable.
d) Name. It's a categorical variable.
e) Count. It's a quantitative variable.

##Problem 1.2

To be a tidy table, each column needs to be a variable containing the same type of value for each case. Number of states is a quantitative variable. However, 'it depends' is not a number, which differs it to other values. 

Also, the format for values should be the same. 'Lincoln, Abraham' should be 'Abraham Lincoln'.

We should also seperate the two numbers in the in office variable. '1837 to 1841' and '1837-1841' are not the same.

## Problem 1.4

1.
In Table A, variables are Year, Algeria, Brazil and Columbia.
In Table B, variables are Country, Y2000 and Y2001.
In Table C, variables are Country, Year and Value.

2.
For Table A, a case is a year.
For Table B, a case is a country.
For Table C, a case is a country in a year.

## Problem 1.5

1. There are six variable, including 'faa', 'name', 'lat,lon', 'alt', 'tz', 'dst'.
2. A case is an individual airport.
3. faa is a categorical variable. name is categorical. lat is quantitative. alt is quantitative. tz is categorical. dst is categorical.


##Problem 2.2

File name should be wrapped in quotes.


##Problem 2.3
```{r}
help("CPS85")
```

CPS stands for The Current Population Survey, which is used to supplement census information between census years. It contains worker's wages, sex, years of education, years of work experience, occupational status, regino of residence and union membership.


##Problem 2.4
```{r}
help(NHANES, package <- "NHANES")
```

Instead of naming NHANES as package, we should use named argument package = "NHANES". 

##Problem 2.6

2. first-essay. Punctuation symbol is not allowe in object name except . and _ .
3. "MyData". Object names are never in quotes.
5. small sample. There should be no space in object name.
9. sqrt(). There should be no punctuation symbol in an object name.

##Problem 2.7
```{r}
data(flights, package="nycflights13")
flights%>% nrow()
dim(flights)
```

1. 
There are 19 variables.

2. There are 336776 cases.

3. A case is an individual flight.

4. Year, month, day, dep_time, sched_dep_time,  arr_time, sched_arrive_time, carrier, flight, tailnum, origin, dest,time_hour are categorical.
Arr_delay, dep_delay, air_time, distance, hour, minute are quantitative.

5. The unit for air_time is minutes , for distance is miles.


##Problem 2.8

a) Improprt syntax for function argument

b) No assignment operator

c) Invalid object name

d) Unmatched quotes in character string

e) No mistake

##Problem 2.9

Only . and _ can be used in the object name.

All the characters can be used in a quoted character string.


##Problem 2.10

```{r}
dim(CountryData)
```
There are 76 variables in CountryData.


```{r}
help(NCHS)
```
tfat measures the mass of trunk fat.


```{r}
WorldCities %>% nrow()
```
There are 23018 cases.


```{r}
BabyNames %>% names()
```
The third variable is count.


```{r}
help(RegisteredVoters)
```
DEM stands for Democratic. LIB stands for Libertarian. REP stands for Republican. UNA stands for Unaffiliated.


##Problem 3.1

1) a data frame, e.g. fireplace <- BabyNames %>% filter(sex == "F")

2) a function, e.g. fireplace()

3) the name of a named argument, e.g. functionverb(fireplace=sum(4,5))

4) a variable, e.g. mean(fireplace)

##Problem 3.2

```{r}
Result <- BabyNames %>% filter(name=="Prince")
```

```{r}
Result <- filter(BabyNames, name=="Prince")
```

If this is a chaining pattern, the name of the dataset should be in the front, followed by %>%.

If this is a non-chaining patter, we should not use %>%.

##Problem3.3

Instead of naming NHANES as package, we should use named argument package = "NHANES". 

##Problem 3.4

1) BabyNames (b)
2) filter (a)
3) name (c)
4) == (a)
5) group_by (a)
6) year (c)
7) sex (c)
8) summarize (a)
9) yearlyTotal (d)
10) sum (a)
11) count (c)
12) ggplot(a)
13) aes (a)
14) x (d)
15) y (d)
16) geom_point (a)
17) color (d)
18) geom_vline (a)
19) xintercept (d)

##Problem 3.5
```{r}
data(msleep, package="ggplot2")
msleep%>% nrow()
```

brainwt means the brain weight in kilograms. 

There are 83 cases.

A case is a kind of animals.

The vore variable can be carnivore, omnivore or herbivore.

##Problem 3.6

c) finds the mean other than the sum.

##Problem 4.1

*one* italic

**two** bold

* three bullet point

# Four Header (first-level)

`five` monospaced text in grey shade (Inline R code)

## Six Header (second-level)

[seven](http://tiny.cc/dcf/index.html) a link that direct to the website


##Problem 4.2

a) Use ``` instead of '''.

b) Use ``` instead of """, use {} other than ()

c) Missing a ` in closing.

d) Opening and Closing delimiter should be in different sentence.

e) Should only be 3 ` other than 4 in closing delimiter.

##Problem 4.3

An introduction as a header. The word "easy" in italic. R will also calculate 5.

##Problem 4.4

1. A possible URL; can also be a file name
2. A possible file
3. Neither.http other than ptth
4. A possible URL.
5. A possible URL. // is weird.
6. A possible URL or file