# Week 7 Short Answer Questions

## Nana Adom Mills-Robertson

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->
**15.1**
```{r}
lubridate::mdy("November 21, 1995") - lubridate::mdy("April 30, 1777")

lubridate::mdy("November 21, 1995") - lubridate::mdy("06-23-1912")

lubridate::dmy("21 November 1995") - lubridate::dmy("3 March 1847")

lubridate::mdy_hm("Nov. 21, 1995 at 11:00 am") - lubridate::mdy_hm("11 am on Nov. 11th, 1918 at 11:00 am")

lubridate::mdy("November 21, 1995") - lubridate::mdy("July 20, 1969")
```

**15.2**

tidyr:extract_numeric("42,659.30")

tidyr::extract_numeric("17%")

neither works here

tidyr::extract_numeric("£100")

tidyr::extract_numeric("9.8 m/seconds-square")

tidyr::extract_numeric("9.8 m/sˆ2")

N/A neither works for this one

as.numeric("6.62606957e-34")

tidyr::extract_numeric("42.659,30 (A European style)")

**16.1**

```{r}
BabyNames %>%
  filter(sex == "M") %>%
  group_by(name) %>%
  summarise(total = sum(count)) %>%
  filter(grepl("[aeiou]$", name)) %>%
  arrange(desc(total)) %>%
  head(10)
```

```{r}
BabyNames %>%
  group_by(name) %>%
  summarise(total = sum(count)) %>%
  filter(grepl(".*(jo$|joe$)", name)) %>% 
  arrange(desc(total)) %>%
  head(10)
```


**16.2**

An American phone number

**16.3**

a. Two letters

b. They seem to be US states, comprised of two letters. However there are many combinations that don't represent US states and could mean something else; other areas of America that are not state level. 

c. I believe that the pattern is trying to express the short-hand for US states. 



 