# Week 6 Project

## Josh Marcus

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

```{r cache = TRUE}
data_site <- "http://tiny.cc/dcf/2014-Q4-Trips-History-Data-Small.rds"
Trips <- readRDS(gzcon(url(data_site)))
```

##1
```{r}
Trips %>%
  ggplot(aes(x = sdate)) +
  geom_density()
```

##2
```{r}
Trips %>%
  mutate(time_of_day = lubridate::hour(sdate) 
         + lubridate::minute(sdate) / 60) %>%
  group_by(time_of_day) %>%
  arrange(desc(time_of_day)) %>%
  ggplot(aes(x = time_of_day)) +
  geom_density()
```

##3
```{r}
Trips %>%
  mutate(time_of_day = lubridate::hour(sdate) 
         + lubridate::minute(sdate) / 60) %>%
  mutate(day_of_week = lubridate::wday(sdate)) %>%
  group_by(time_of_day) %>%
  arrange(desc(time_of_day)) %>%
  ggplot(aes(x = time_of_day)) +
  geom_density() + 
  facet_wrap( ~ day_of_week)
```

##4
```{r}
Trips %>%
  mutate(time_of_day = lubridate::hour(sdate) 
         + lubridate::minute(sdate) / 60) %>%
  mutate(day_of_week = lubridate::wday(sdate, label = TRUE)) %>%
  group_by(time_of_day) %>%
  arrange(desc(time_of_day)) %>%
  ggplot(aes(x = time_of_day)) +
  geom_density(aes(color = client)) + 
  facet_wrap( ~ day_of_week)
```

##5
```{r}
#Trips %>%
  #mutate(time_of_day = lubridate::hour(sdate) 
         #+ lubridate::minute(sdate) / 60) %>%
  #mutate(day_of_week = lubridate::wday(sdate, label = TRUE)) %>%
 # group_by(time_of_day) %>%
  #arrange(desc(time_of_day)) %>%
  #ggplot(aes(x = time_of_day)) +
  #geom_density(position = position_stack)) + 
  #facet_wrap( ~ day_of_week)
```

Not sure exactly how to input 5, but from what I read online, it looks like it takes out cases where there is missing data, so I would argue 5 is the most effective, informative way of presenting the data, for it gives you many different dimensions to consider all at once (client/vs. casual, date, time), and it cuts out cases with spotty data.

