# Week 3 Short Answer Questions

## Qiuhan

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

Problem 5.1

```{r}
library(mosaicData)
#barGraphHelper(CPS85)
ggplot(data=CPS85,aes(x=sex,y=wage ,fill=married))+geom_bar(stat='identity',position='dodge', width=.9) 
```


5.2
```{r}
WorldMap(HappinessIndex, key=country, fill=corruption)
```

6.5

b. State and polling organization.

6.6

d. Glyph is rectangle and graphical attribute is color and text.

6.7
a) State

6.8
```{r}
Small <-NCHS %>%sample_n(size=5000)
#scatterGraphHelper(Small)
ggplot(data=Small,aes(x=bmi,y=weight))+geom_point()+aes(colour=smoker) 
```

Each dot represents a person, showing the person's bmi and weight. Color pink means that the person is not a smoker; blue means the person is.

7.1

a. mean()
b. mutate(variableA/variableB)
c. arrange(dataset, desc(variable))
d. filter()
e. select(datatable, A, X)
f. group_by(A,B) and summarize(mvalue=max(X))

7.4
a)
```{r}
#BabyNames %>%group_by( First ) %>% summarise( votesReceived=n() )
```
don't need to quote First. Dataset is wrong.

b)
```{r}
#Tmp <- group_by(BabyNames, year, sex ) %>% summarise( Tmp, totalBirths=sum(count))
```
You cannot call Tmp within the statement.

c)
```{r}
#Tmp <- group_by(BabyNames, year, sex)summarise( BabyNames, totalBirths=sum(count) )
```
There's no link between the two verbs.

7.5

a) arrange(sex, count)
b) filter(sex=="F")
c) filter(sex=="M",count>9)
d) summarise(total = sum(count))
e) select (name, count)

7.7
a)
```{r}
BabyNames %>%group_by(year, sex) %>% summarise(total = sum(count))
```
Do not need to call BabyNames inside the verbs.

b) 
```{r}
ZipGeography %>% group_by(State) %>% summarise(pop = sum(Population))
```
should use %>% other than <-

c)
```{r}
Minneapolis2013 %>% group_by(First) %>%summarise(voteReceived = n())
```
should use %>% other than <-

d) 
```{r}
Minneapolis2013 %>% group_by(First) %>%summarise(votesReceived = n()) 
```
Put Minneapolis2013 at the front, then group_by, then summarise.

7.11
a) sex, count (total number of patients with that sex), meanAge (average age of patients of that sex)

b) diagnosis, count (total number of patients with that diagnosis), meanAge (average age of patients of that diagnosis)

c) sex, diagnosis, count (total number of patients with that sex and that diagnosis), meanAge (average age of patients of that sex and that diagnosis)

d) age, diagnosis, count (total number of patients with that age and that diagnosis), meanAge (average age of patients of that age and that diagnosis)

e) age, count (total number of patients at that age), meanAge (should be the age)

7.12
1. nrow()
2. names()
3. help()
4. library()
5. group_by()
6. summarise()
