# Week 6 Short Answer Questions

## Lang Li

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

# Question 12.1

```{r}
BabyNames %>% group_by(sex,name) %>% summarise(all_names = sum(count))%>% mutate(popularity = rank(desc(all_names))) %>% filter (popularity <=5)
```

# Question 12.2

```{r}
Popular <- BabyNames %>% group_by(year,name) %>% summarise(total = sum(count))%>% mutate(ranking = ifelse(rank(desc(total)) <= 100,"top_100","notTop100")) %>% group_by(year,ranking) %>% summarise(total = sum(total))

GlyphReady <- Popular %>% spread(ranking, total) %>% mutate(frac_in_top_100 = top_100 / (top_100 + notTop100))

GlyphReady %>% ggplot(aes(x=year, y=frac_in_top_100)) + geom_line() + ylim(0, NA)
```

# Question 12.3

a. Summary function

b. Neither of them.

c. Summary function

d. Transformation function

e. Transformation function

f. Summary function

g. Transformation function

h. Summary function

# Question 13.1

1. There are China, Japan, USSR, Germany, US, France and Italy. A total of 7 distinct vertices.

2. There are 9 edges since there are 9 "from-to" relationships.

# Question 13.2

1. The vertices are A, B, C, D.

2. Table 2 is the correct one.

3. For Table 1, there is not BC relationship and for Table 3, you cannot have a edges that links three things,

# Question 13.3

Table 2 gives the information!

# Question 13.4

1. exports.

2. Population. (pop)


# Question 14.1

```{r}
CPS85 %>% ggplot(aes(sex, wage)) +geom_boxplot(aes(fill = sex))
```

# Question 14.3

I can see the peak for woman is about 1.61 m and for men is about 1.76m.

# Question 14.7

```{r}
CPS85 %>% ggplot(aes(educ, wage, color = sex)) + geom_point(na.rm=TRUE) + stat_smooth(method = "lm", na.rm = TRUE) + ylim(0,15)
```

# Question 14.10

```{r}
Galton %>%  ggplot(aes(x = height)) + geom_density(aes(fill = sex), alpha = 0.2) + theme(legend.position="right") + scale_fill_manual( values = c("black","aquamarine1"))
```

