# Week 3 Project

## Shelby Witherby

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->
```{r}

library(DataComputing)
library(mosaicData)

```

```{r eval = FALSE}
scatterGraphHelper(CPS85)

```

```{r eval = FALSE}
scatterGraphHelper(NCHS)
```


```{r}

ggplot(data = CPS85, aes(x=exper, y=wage, color = married)) + geom_point() + facet_wrap( ~ sector)


```

```{r}
ggplot(data = NCHS, aes(x = bmi)) + geom_density(aes(color = sex, fill = sex), alpha = .3) + facet_wrap(~ pregnant)
```


```{r}

diamonds %>%
  group_by(color) %>%
  summarise(ave = mean(carat)) %>%
  arrange(desc(ave)) %>%
  head(1)


```

```{r}

diamonds %>%
  group_by(clarity) %>%
  summarise(ave = mean(table)) %>%
  arrange(desc(ave)) %>%
  head(1)
```
## Diamonds
# 1. J color diamonds seem to be largest on average
# Diamonds with a clarity of I1 have an average table of 58.3


```{r}

Minneapolis2013 %>%
  group_by(Second) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  head(5)
```
```{r}
Minneapolis2013 %>%
  group_by(First) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  head(10)
```
```{r}
Minneapolis2013 %>%
  group_by(Third) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  head(5)
```


## Voting
# 1. In Minneapolis2013, there are 80101 cases
# 2. The top 5 candidates in the Second vote selections are: Betsy Hodges, Don Samuels, Mark Andrew, undervote, Jackie Cherryhomes
# 3. In the First vote selections, there were 834 marked undervote. In the Second vote selections, there were 10598 marked undervote. In the Third vote selections, there were 19210 marked undervote. 

