# Week 4 Short Answer Questions

## Josh Marcus

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

##Chapter 8
#8.1
a) geom_point() 2) adds a layer of glyphs
b) geom_histogram() 2) adds a layer of glyphs
c) ggplot() 1) Constructs the graphics frame
d) scale_y_log10() 5) Changes the scale for the frame
e) ylab() 3) Sets an axis label
f) facet_wrap() 4) divides the frame into facets
g) geom_segment() 2) adds a layer of glyphs
h) xlim() 5) changes the scale for the frame

#8.2
#1 

```{r}
CPS85 %>%
  ggplot(aes(x = age, y = wage, shape = married)) +
  geom_point() +
  facet_wrap( ~ sector)
```

#2

```{r}
CPS85 %>%
  ggplot(aes(x = age, y = wage)) +
  geom_point() +
  facet_grid(sex ~ married) 
  
```

#8.3

A)
```{r}
CPS85 %>%
  ggplot(aes(x = age, y = wage)) +
  geom_point() 
```

B)

```{r}
CPS85 %>%
  ggplot(aes(x = age, y = wage, shape = sex)) +
  geom_point() 
```

C)

```{r}
CPS85 %>%
  ggplot(aes(x = age, y = wage, shape = sex)) +
  geom_point() +
  facet_grid(married ~ . )
```

D)

```{r}
CPS85 %>%
  ggplot(aes(x = age, y = wage, shape = married)) +
  geom_point() 
```

##Chapter 9
#9.1
a) str() is a quick presentation
b) group_by() is a data verb
c) rank () is a transformation
d) mean() is a summary function
e) filter() is a data verb
f) summary() is a quick presentation
g) summarise() is a data verb
h) anti_join() is a transformation
i) merge() is a data verb
j) glimpse() is a quick presentation

#9.3

#1

```{r}
diamonds %>%
  group_by(color) %>%
  summarise(size=mean(carat, na.rm = TRUE)) %>%
  arrange(desc (size)) %>%
  head (1 )
```

J-colored diamonds seem to be largest in terms of carats.

#2

```{r}
diamonds %>%
  group_by(clarity) %>%
  summarise(
    ave_table = mean(table, na.rm = TRUE)) %>%
  arrange(desc (ave_table)) %>%
  head (1)
```

I1 clarity diamonds have the largest average table per carat.
