# Week 3 Short Answer Questions

## Micheala Sharp!

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->


#5.1
```{r}
library(mosaicData)
library(DataComputing)
ggplot(data=CPS85,aes(x=sex,y=wage ,fill=married))+geom_bar(stat='identity',position='dodge', width=.9)+ facet_wrap(~race,ncol=3) 
```

#5.2 
```{r}
library(mosaicData)
library(DataComputing)
WorldMap(key="country", fill="corruption", HappinessIndex)
```

#6.5 
###state on the y axis, organization on the x axis

#6.6 
###a. plain black font 
###b. the logos 
###c. the polling results 
###d. The numbers for polling  

#6.7 
###a. verticle axis 
###b.horiznotal axis   
###c. color 
###d. color and font 

#6.8 **** 
```{r}
Small<-
  NCHS %>%
  sample_n(size=5000)
ggplot(data=Small,aes(x=bbmi,y=weight,color=smoker))+geom_point()
```


#7.1
###a. summarise() -average 
###b.mutate() adds new column that is a ratio between two variables 
###c. arrange() creates new data table 
###d. filter() new data table that fits the criteon 
###e. select() table with three variable A , B, C, and quan X and product just A and X
###f. group_by() and summerise() dcreate sepereate cases for exch catagorical variable 

#7.4
###a. there is no variable called first 
###b. there is no need to put BabyNames and Tmp as arguments 
###c. %?%

#7.5
###a. arrange(sex,count)
###b. filter(sex=="F")
###c. filter(sex == "M", count >10 )
###d. summarise(total = sum(count))
###e. select(name,count)


#7.11
###a. two columns one for male and female and the count of how many of them share the samne mean age
###b. colums seperated by diagnosis and the count by mean age 
###c. sex and diagnosis with count mean age
###d. age and diagnosis with count of mean age 
###e. age and count divided by the mean age 

#7.12
###1. count the number of cases in a data table - *nrow()* 
###2. list the names of the variable in a data table - *names()*
###3. for data tables show the code book -*help()*
###4. load a package into R -*library()*
###5. mark a data table as grouped by one or more catagorical variables -*group_by()*
###6. add up, group by group, a wauantitative variable in a data table-*summarise()*







