# Week 7 Short Answer Questions

## Daniel Ochoa

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

## 15.1
My birthday is on March 21st 1996
a) 
```{r}
lubridate::mdy("March 21, 1996") - lubridate::mdy("April 30, 1777") 
```
A time difference of 79948 days

b)
```{r}
lubridate::mdy("March 21, 1996") - lubridate::mdy("06-23-1912") 
```
A time difference of 30587 days

c)
```{r}
lubridate::mdy("March 21, 1996") - lubridate::dmy("3 March 1847") 
```
A time difference of 54440 days

d)
```{r}
lubridate::mdy_hm("Mar. 21, 1996 at 11:00 am") - lubridate::mdy_hm("Nov. 11th, 1918 at 11:00 am") 
```
A time difference of 28255 days

e)
```{r}
lubridate::mdy("March 21, 1996") - lubridate::mdy("July 20, 1969")
```
A time difference of 9741 days


## 15.2
a) as.numeric()
b) tidyr::extract_numeric()
c) Neither
d) tidyr::extract_numeric()
e) tidyr::extract_numeric()
f) tidyr::extract_numeric()
g) tidyr::extract_numeric()
h) as.numeric()
i) as.numeric()


## 16.1
Here I find the top 10 boy baby names ending in a vowel.
```{r}
 BabyNames %>%
 filter(sex == "M") %>%
 group_by(name) %>%
 summarise(total = sum(count)) %>%
 filter(grepl("[aeiou]$", name)) %>%
 arrange(desc(total)) %>%
 head(10)
```

Here I find the top 10 names ending with either 'joe' or 'jo'.
```{r}
 BabyNames %>%
 group_by(name) %>%
 summarise(total = sum(count)) %>%
 filter(grepl(".*(joe$|jo$)", name)) %>% 
 arrange(desc(total)) %>%
 head(10)
```


## 16.2
This entire expression will match U.S. phone numbers. U.S. numbers do not begin with 0 or 1 and they have 10 total numbers, a triplet followed by a triplet followed by a quadruplet. The regex expression will only extract the numbers themselves and not the spaces, dashes, or periods in between. 


## 16.3 

1) All the strings that match the pattern will be two letters long.

2) At most only one string will match.

3) Many of these seem to be abbreviations for U.S. states but there are some outher, FM for instance is not an abbreviation for any U.S. state. 