# Week 2 Project

## Tristan Truttmann

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

(1) Here we analyze the number of books in the data set that Professor Kaplan prepared for this class.  The data was downloaded from the URL "http://tiny.cc/dcf/Library-small.rda".  

### Basics 

```{r}
load("~/Comp-110-Assignments/Library-small.rda")
```

(4) 

```{r}
nrow(Bks)
```

This tells us that the Bks data frame contains 3765 cases. These represent a bunch of books that the library may or may not have.  

```{r}
nrow(Inv)
```

This tells us that the data frame contains 2000 cases.  These represent several book that our library does indeed have.  

```{r}
ncol(Bks)
```

```{r}
ncol(Bks)
```

These two commands tells us that each dataframe has 15 variables.  

(5)

```{r}
Inv %>% group_by(Current.Status) %>% tally()
```

This means that of the books in the data sample that Professor Kaplan has created, 1866 books are available, 1 book is missing, 18 books are on loan, and 115 and currently withdrawn.

(6)

```{r}
Inv %>% group_by(Issued.Count) %>% tally() 
```

This means that, of the sample of Macalster library books that Professor Kaplan created, 996 have never been checked out and 337 have only been checked once, and so on.  
