# Week 7 Short Answer Questions

## Joshua Doyle

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(lubridate)
```
<!-- put your content after this line -->

##15.1

```{r}
lubridate::mdy("November 7, 1995") - lubridate::mdy("April 30, 1977")
```
A Time difference of 6765 days

##b)

```{r}
lubridate::mdy("11-07-1995") -
  lubridate::mdy("06-23-1912")
```
A Time difference of 30452 days

##c) 

```{r}
lubridate::dmy("7 November 1995") -
  lubridate::dmy("3 March 1847")
```
A Time difference of 54305 days

##d) 

```{r}
lubridate::mdy_hm("Nov. 7, 1995 at 11:00 am") -
  lubridate::mdy_hm("11 am on Nov. 11th, 1918 at 11:00 am")
```
Time difference of 28120 days

##e)

```{r}
lubridate::mdy("November 7, 1995") -
  lubridate::mdy("July 20, 1969")
```
Time difference of 9606 days

##15.2 

```{r}
as.numeric(42,659.30)
```
##a) 
as numeric works

##b) 
tidyr::extractnumeric works

##c) 
For nineteen neither works

##d) 
tidyr::extractnumeric works

##e)
tidyr::extractnumeric works

##f)
tidyr::extractnumeric works

##g) 
tidyr::extractnumeric works

##h) 
as numeric works

##i)
as numeric works

##16.1 

```{r}
BabyNames %>%
  filter(sex == "M") %>%
  group_by(name) %>%
  summarise(total = sum(count)) %>%
  filter(grepl("[aeiou]$", name)) %>%
  arrange(desc(total)) %>%
  head(10)
```

##16.1.2

```{r}
BabyNames %>%
  group_by(name) %>%
  summarise(total = sum(count)) %>%
  filter(grepl(".*(jo$|joe$)", name)) %>% 
  arrange(desc(total)) %>%
  head(10)
```

##16.2
The expression seems to be matching a US phone numer. This makes sense looking at the number of digits we have. 

##16.3.1

The strings are two letters long. For example "MN", "WI", "NY"..

##16.3.2 

There seem to be about 61 potential combinations. This is because states and some counties are included. 

##16.3.3

As mentioned above, these are all abbreviations for US states. 


