# Week 3 Short Answer Questions

## Your name should appear here!

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

Here is my content!

5.1 
```{r}
ggplot(data=CPS85,aes(x=educ,y=wage ))+geom_bar(stat='identity',position='stack', width=.9)+ facet_wrap(~married,ncol=3)
```

5.2
```{r}
HappinessIndex %>% WorldMap(key="country",fill="corruption")
```

6.5
b

6.6
d

6.7
d

6.8
```{r}
Small <-
  NCHS %>%
  sample_n(size=5000)
ggplot(data=NCHS,aes(x=bmi,y=weight))+geom_point()+aes(colour=smoker)
```

7.1
summarise

mutate

arrange

filter

select

group_by


7.4
a) quotation marks around "First"

b) Tmp in summarise()

c) BabyNames in group_by()


7.5
arrange(sex, count)

filter(sex=="F")

filter(sex=="M") inner_join(TableB, by = c(name = "name"))

summarise(sum(count))

select(name,count)


7.7
group_by(year, sex)

ZipGeography %>%

group_by(First) %>%

Minneapolis2013 %>%

  group_by(First) %>%
  
  summarise(votesReceived = n())
  
  
7.11

a. sex count meanAge

b. diagnosis count meanAge

c. sex diagnosis count meanAge

d. age diagnosis count meanAge

e. age count meanAge


7.12

n()

names()

help()

library()

group_by()

sum()
