# Week 5 Project

## Tristan Truttmann

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```

```{r}
download.file("http://tiny.cc/dcf/ScorecardSmall.Rda", destfile = "ScorecardSmall.Rda")
load("ScorecardSmall.Rda")
```

(1) 

To create the graphic, I will need the variables `CONTROL`, `ADM_RATE`, `NPT41_PUB`, `NPT41_PRIV`, `NPT43_PUB`, `NPT43_PRIV`, `NPT45_PUB`, and `NPT45_PRIV`.  To demonstrate this explicitly, I will drop the unneeded terms: 

```{r}
CleanScorecard <- ScorecardSmall %>%
  select(CONTROL, ADM_RATE, NPT41_PUB, NPT41_PRIV, NPT43_PUB, NPT43_PRIV, NPT45_PUB, NPT45_PRIV)
```

(2)

```{r}
NarrowCleanScorecard <- CleanScorecard %>%
  gather(key=IncomeLevel,value=net_cost,NPT41_PUB, NPT41_PRIV, NPT43_PUB, NPT43_PRIV, NPT45_PUB, NPT45_PRIV)
head(NarrowCleanScorecard)
```

(3) 

First I will download the key you gave me:

```{r}
income_key = read.csv("http://tiny.cc/dcf/NPT4-names.csv")
```

Then I will crate a new table that has the ``new`` names: 

```{r}
NarrowCleanScorecard2 <- NarrowCleanScorecard %>%
  inner_join(income_key,by = c("IncomeLevel" = "long_name"))
```

### Creating the final graph: 

Now I will do some filtering to remove `CONTROL=3`: 

```{r}
NarrowCleanScorecard3 <- NarrowCleanScorecard2 %>%
  filter(CONTROL != 3)
```

```{r}
NarrowCleanScorecard3 %>%
  ggplot() +
  geom_point(aes(x = ADM_RATE,y = net_cost,color="#56B4E9")) +
  facet_grid( CONTROL ~ short_name ) + 
  xlab("Admissions rate") + 
  ylab("Net cost per year $'000") + 
  stat_smooth(aes(x = ADM_RATE,y = net_cost))
```

Great!  As you can see 1 is public and 2 represents private institutions.  I could make this a little bit more similar to the economist graph, but I think this would be inefficient with my limited time.  






