# Week 7 Short Answer Questions

## Kai Heen

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(lubridate)
```
<!-- put your content after this line -->

## 15.1
```{r}
lubridate::mdy("November 17, 1995") - lubridate::mdy("April 30, 1977")
```



b)

```{r}
lubridate::mdy("11-17-1995") -
  lubridate::mdy("06-23-1912")
```


c)

```{r}
lubridate::dmy("17 November 1995") -
  lubridate::dmy("3 March 1847")
```



d)

```{r}
lubridate::mdy_hm('Nov. 17, 1995 at 11:00 am') -
  lubridate::mdy_hm("Nov. 11th, 1918 at 11:00 am")
```


e)

```{r}
lubridate::mdy("November 17, 1995") -
  lubridate::mdy("July 20, 1969")
```

## 15.2

a)

as numeric

b)

tidyr::extract_numeric 

c)

Neither

d)

tidyr::extract_numeric

e)

tidyr::extract_numeric

f)

tidyr::extract_numeric

g)

tidyr::extract_numeric

h)

as numeric

i)

as numeric

## 16.1


```{r}
BabyNames %>%
  filter(sex == "M") %>%
  group_by(name) %>%
  summarise(total = sum(count)) %>%
  filter(grepl("[aeiou]$", name)) %>%
  arrange(desc(total)) %>%
  head(10)
```

```{r}
BabyNames %>%
  group_by(name) %>%
  summarise(total = sum(count)) %>%
  filter(grepl(".*(jo$|joe$)", name)) %>% 
  arrange(desc(total)) %>%
  head(10)
```


## 16.2

This expression will match a US phone number. US numbers have 10 digits, and cannot start with 0 or 1.

## 16.3

1)

All matching strings are 2 letters long.

2)

There seem to be 61 total matches

3)

These seem to represent US states and territories.