# Week 2 Short Answer Questions

## Your name should appear here!

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->



Here is my content!

1.1,

a) 3
b) 2
c) 1
d) 2


1.2,

'it depends' is a categorical entry for a quantitative variable. Also, the format for years in office is not entered consistently.

1.3,

Replace 1837 to 1841 with 1837-1841. Relable 'number of states' to 'peak number of states in union', and enter values corresponding to the maximum number of states in the union during each case.

1.4

1.
The year, the names of countries, and corresponding values.
2.
A) In table A, a case is a selected year
b) In table B, a case is a country
c) In table C, a case is a country in a year


1.5



2.2,

file name

2.3,

Data from the 1985 Current Population Survey

2.4,

The help function only needs one argument, the name of the package.

2.6,

2. Cannot include '-' character
3. no quotation marks
5. no spaces
8. can't start with a period
9. Needs an argument

2.7,

flights has 19 variables. There are 336776 cases. Each case represents one flight. All variables are quantitative with the exception of the carrier, origin, destination, and arguably the flight number (depending on how they assign flight numbers). The units for air_time and distance are minutes and miles (or kilometers, not labeled) respectively.

2.8, 

a. Improper syntax
b. No assignment operator
c. Invalid object name (can't start with a number)
d. Unmatched quotes
e. No mistake. The data function does not require an argument.

2.9, 

Only periods and underscores can be used in the name of R objects. All of the characters can be used in a string.

2.10

3.1, 3.2, 3.3, 3.4, 3.5, 3.6
*I did all the chapter three problems, but I forgot to commit then to github. In order to follow the 3 hour rule I will not correct this mistake and continue to chapter four.*

4.1,



*one*
italics
**two**
bold
# four
don't see difference
'five'
don't see difference
##six
don't see difference
[seven](http://tiny.cc/dcf/index.html)
this becomes a link

4.2,

(a) Single quotes don't work
(b) double quotes don't work
(c) need three ticks to close chunk
(d) Need to close chunk on line of its own
(e) Too many closing ticks

4.3,

### Introduction

Arithmetic is *easy!*
```{r}
3+2
```

4.4,

1. Neither
2. possible file
3. neither
4. URL
5. Neither
6. possible url

4.5


