# Week 6 Short Answer Questions

## Joshua Doyle 

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

Here is my content!

##12.1 

```{r}
Top5 <-
  BabyNames %>% 
  group_by(sex,name) %>%
  summarise(TotalCount = sum(count)) %>%
  filter(rank(desc(TotalCount))<=5)
Top5

```


##12.2 

```{r}
Fraction100 <-
  BabyNames %>%
  group_by(year, name) %>%
  summarise(total = sum(count)) %>%
  mutate(Frac10 = ifelse(rank(desc(total)) <= 100, "True", "False" )) %>%
  group_by(year, Frac10) %>%
  summarise(total = sum(total))
Fraction100

```

```{r}
GlyphReady <-
  Fraction100 %>% 
  spread(Frac10, total) %>%
  mutate(Frac10 = True / (True + False))
```

```{r}
ggplot(data = GlyphReady, aes(x = year, y = Frac10)) + 
  geom_point()
```  


##12.3

**a)** summary 
**b)** summary function 
**c)** summary 
**d)** transformation 
**e)** transformation 
**f)** summary 
**g)** transformation 
**h)** summary


##13.1

There are 8 vertices and 9 edges. 

##13.2 

**1)** A,B,C,C
**2)** Table 2
**3)** In Table 1, B C aren't connected as an edge. In Table 3, vertice A isn't directly compared to vertice D. 

##13.3

Table 2 gives the accurate information. 

##13.4

**1)** Exports 
**2)** Population

##14.1

```{r}
library(mosaicData)
CPS85 %>%
  ggplot(aes(x = sex, y = wage)) +
  geom_boxplot(aes(fill=sex))
```

##14.3

For men the most likely height is about 1.75meters, while for women the most likely height is slightly less at 1.6 meters. 


##14.7

```{r}
  ggplot(CPS85, aes(x = educ, y = wage, color = sex)) +
  geom_point() +
  stat_smooth(method="lm") 
```


##14.10 

```{r}
ggplot(Galton, aes(x = height)) +
  geom_density(aes(fill=sex,color=sex), alpha=0.5)

```


